---
title: 'Data cleaning 2: PARDI'
author: "Rosie Watts"
date: "24/07/2021"
output: word_document
---


#Set up R Markdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment 
```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Set current date 
```{r current date}
date <- Sys.Date()
```

Install necessary packages
```{r install packages}
#install.packages("summarytools")
#install.packages("zscorer")
#install.packages("tidyverse")
#install.packages("childsds")
```

+++CH: In general it's good to only load the packages that you really need to avoid conflicts between the packages

Load necessary packages 
```{r load packages}
library(xlsx)
library(summarytools)
library(zscorer)
library(gt)
library(childsds)
library(tidyverse)
```

Read in merged dataset
```{r read in merged data}
arfid_dat <- readRDS(file = "../data/ARFID_data_dem_cleaned2021-08-18.rds")
```

#Inspect data
```{r structure}
arfid_dat %>% 
  str()
```


#PARDI Data Cleaning

Weight, Height and BMI

#Height: 
Inspect height reporting 
```{r inspect height variables}
arfid_dat %>% 
  select(pardi.parent.pre.measurement_select_preferred_unit_height, 
         pardi.parent.pre.what_is_your_childs_height_unc,     #metres
         pardi.parent.pre.what_is_your_childs_height.1_unc,   #cm
         pardi.parent.pre.what_is_your_childs_height.2_unc,   #foot
         pardi.parent.pre.what_is_your_childs_height.3_unc    #inches
  )
```
## Height in metres

Weight is set up to be metres + cms

I manually checked height and some had entered in metres and cms 
E.g., 1 metres, 47 cms, 
Others had entered in both metres and cms 
E.g., 1.47metres, 147cms

Need to set one reporting (m or cm) to 0 - 
so that metres and cms can be added to give patient's height. 

I manually checked each entry to make sure I could recode to 0 and it wouldn't 
effect any other reporting

Check frequencies
+++CH: I have moved the checking here to its own chunk
```{r height in metres checking}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height_unc)
```


Recode height in metres, remove characters and make variable numeric
```{r recode height in metres}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.what_is_your_childs_height_m_unc = 
           recode(pardi.parent.pre.what_is_your_childs_height_unc, 
                  '1m' = "1",
                  '1.09m' = "1.09",
                  'N/A' = "0",       #entered full height in cm  
                  '?' = "0",         #entered full height in cm
                  'will come back' = NA_character_) %>%    
  as.numeric())

arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height_m_unc)
```

## Height in centremetres 

Recode cm and convert to numeric metres 
Manually checked each entry
```{r height in cm checking}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height.1_unc)
```

Recode to 0 - so that they can be added to metres to give full height
```{r recode cm and convert to metres}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.what_is_your_childs_height_cm_unc = 
           recode(pardi.parent.pre.what_is_your_childs_height.1_unc, 
                  '109cm' = "0",  #entered full height in metres
                  '62cm' = "62",
                  '138cm' = "138", #0 in metres
                  '128cm' = "0",  #entered full height in metres
                  '165' = "0",    #entered full height in metres
                  '159' = "0",    #entered full height in metres
                  '110' = "0",    #entered full height in metres
                  '127' = "0",    #entered full height in metres
                  '140' = "0",    #entered full height in metres
                  '128' = "0",    #entered full height in metres 
                  '158' = "0",    #entered full height in metres
                  '94cm' = "0",   #entered full height in metres
                  'will come back' = NA_character_, 
                  'N/A' = NA_character_) %>% 
           as.numeric())

#Divide by 100 to convert to metres (to add to metres to give full weight)

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.what_is_your_childs_height_cm_m_unc =
           (pardi.parent.pre.what_is_your_childs_height_cm_unc/100))

#Check frequency
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height_cm_m_unc)
```

+++CH: There are two participants 1.38 and 1.46 that have entered their whole height in cms. How are you handling those?
+++RW: 1.38 had a '?' in metres column which was recoded to 0
+++RW: 1.46 had 'N/A' in metres column which was also recoded to 0


+++CH: The one who has entered a 2 and is now 0.02; are we sure they mean 2 centimetres? Just double checking
+++RW: I did not check this with the clinicians, but 1.02 metres is an average height for a 4.5 year old
+++CH: You could double check this to see if the BMI z score is fine?

```{r check height 1.02m}
arfid_dat %>% 
  select(ARFID_ID, 
         child.parent.pre.age_yrs,
         pardi.parent.pre.what_is_your_childs_height_m_unc,
         pardi.parent.pre.what_is_your_childs_height_cm_m_unc
         ) %>% 
  filter(pardi.parent.pre.what_is_your_childs_height_cm_m_unc == 0.02)
```


## Height in feet (ft)

```{r height in feet checking}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height.2_unc)
```

Recode height in feet and inches and convert to numeric
```{r recode height in feet}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.what_is_your_childs_height_ft_unc = 
           recode(pardi.parent.pre.what_is_your_childs_height.2_unc, 
                  '6 foot' = "6",
                  '5’' = "5",
                  'Not sure' = NA_character_) %>%    
  as.numeric())

arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height_ft_unc)
```

## Height in inches

```{r height in inches checking}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height.3_unc)
```

Recode height in inches and covert to numeric
```{r recode height in inches}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.what_is_your_childs_height_inches_unc = 
           recode(pardi.parent.pre.what_is_your_childs_height.3_unc, 
                  'Not sure' = NA_character_) %>%    
  as.numeric())

arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height_inches_unc)
```


## Convert all height data to metres 

+++CH: see my comment about !is.na()
+++RW: when I use !is.na() it makes the variable NA? 
I adapted the current script from yours and Helena's BMI script in the Ilovedata github which used is.na?  
```{r convert height to m}
arfid_dat$pardi.parent.pre.what_is_your_childs_height_metres_unc <- NA


arfid_dat <- arfid_dat %>%
  mutate(
      # Convert feet and inches to metres
    pardi.parent.pre.what_is_your_childs_height_metres_unc =
      if_else(
        condition = 
          is.na(pardi.parent.pre.what_is_your_childs_height_metres_unc), 
        # +++CH: here I would work with !is.na()
        true = 
          #convert ft and inches to height in metres
          (pardi.parent.pre.what_is_your_childs_height_ft_unc*0.3048) + 
          (pardi.parent.pre.what_is_your_childs_height_inches_unc*0.0254), 
        false = NA_real_,
        missing = NA_real_
        ),
         
         #Add metres and cm to give height in metres
         pardi.parent.pre.what_is_your_childs_height_metres_unc = 
          if_else(condition = is.na(pardi.parent.pre.what_is_your_childs_height_metres_unc),
                          true = (pardi.parent.pre.what_is_your_childs_height_m_unc +
                                    pardi.parent.pre.what_is_your_childs_height_cm_m_unc),
                          false = pardi.parent.pre.what_is_your_childs_height_metres_unc,
                          missing = NA_real_
                          ))

arfid_dat %>% 
  descr(pardi.parent.pre.what_is_your_childs_height_metres_unc) 
```

Clean weight in metres

+++CH: save this min max values in their own variables
```{r remove implausible values}
arfid_dat <- arfid_dat %>% 
  mutate(
    pardi.parent.pre.what_is_your_childs_height_metres =  
      case_when(
        pardi.parent.pre.what_is_your_childs_height_metres_unc > .50 &
          pardi.parent.pre.what_is_your_childs_height_metres_unc < 3.00
        ~ pardi.parent.pre.what_is_your_childs_height_metres_unc
        )
         )

arfid_dat %>% 
  descr(pardi.parent.pre.what_is_your_childs_height_metres)
```

```{r}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_height_metres)
```

+++CH: How many implausible values do you have? 
+++RW: This removed 1 value (7 metres)
+++CH: What may have gone wrong with the implausible values?
+++RW: Reporting error - entered 600 cms (may have meant 60cms = 1.60m)


Create a height variable in centimetres for z-scorer package
```{r height in cms}
arfid_dat <- arfid_dat %>%
  mutate(pardi.parent.pre.what_is_your_childs_height_cm = 
           pardi.parent.pre.what_is_your_childs_height_metres*100)

arfid_dat %>% 
  descr(pardi.parent.pre.what_is_your_childs_height_cm)
```


# Weight: 

Recode: 'Please select your preferred unit of measurement for upcoming weight-related questions'
to the corresponding measurement options (data dictionary)
```{r preferred weight measurement}
arfid_dat %>%
  select(
    pardi.parent.pre.measurement_select_preferred_unit_weight, 
    pardi.parent.pre.what_is_your_childs_weight_unc,      #lbs
    pardi.parent.pre.what_is_your_childs_weight.1_unc,    #kg
    pardi.parent.pre.what_is_your_childs_weight.2_unc,    #stone &
    pardi.parent.pre.what_is_your_childs_weight.3_unc    #lbs
    )
```

## Weight in pounds

Check weight in pounds
```{r weight in lbs checking}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_weight_unc)
```

Filter age and check weight in lbs is feasible
```{r age and weight in pounds}
arfid_dat %>% 
  select(ARFID_ID, 
         child.parent.pre.age_yrs_dec_unc,
         pardi.parent.pre.what_is_your_childs_weight_unc) %>% 
  filter(pardi.parent.pre.what_is_your_childs_weight_unc == "5 stone11" | 
         pardi.parent.pre.what_is_your_childs_weight_unc == "67" |
         pardi.parent.pre.what_is_your_childs_weight_unc == "76.31")
```

+++CH: I don't understand what you are doing here
+++RW: Recode height to pounds as it is in the lbs column 
weight in stone * 14 = weight in lbs
5.11 * 14 = 71.54
```{r recode weight in lbs}
arfid_dat <- arfid_dat %>% 
  mutate(
    pardi.parent.pre.what_is_your_childs_weight_lbs_unc = 
      recode(
        pardi.parent.pre.what_is_your_childs_weight_unc,
        '5 stone11' = "71.54"
        ) %>% 
           as.numeric()
    )
         
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_weight_lbs_unc)
```

## Weight in kg

```{r weight in kg checking}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_weight.1_unc)
```


Recode weight in kg and make numeric
```{r recode weight in kg}
arfid_dat <- arfid_dat %>% 
  mutate(
    pardi.parent.pre.what_is_your_childs_weight_kg_unc = 
      recode(pardi.parent.pre.what_is_your_childs_weight.1_unc, 
             '15.33kg' = "15.33",  
             '15.400kg' = "15.4",
             '31.2 kg' = "31.2",
             'will come back' = NA_character_ 
                  ) %>% 
           as.numeric()
    )

arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_weight_kg_unc)
```

Check weight in stone and pounds
```{r check weight in stone and lbs}
arfid_dat %>% 
  select(
    pardi.parent.pre.what_is_your_childs_weight.2_unc, 
     pardi.parent.pre.what_is_your_childs_weight.3_unc
    ) %>% 
  freq()
```
No cleaning needed. 


##Convert all weight reportings to kg
+++CH: change to !is.na() 
++RW: this sets all variables to NA? 
```{r convert weight to kg}
arfid_dat$pardi.parent.pre.what_is_your_childs_weight_kg_merged <- NA

#convert weight in stone and lbs to kg

arfid_dat <- arfid_dat %>%
  mutate(pardi.parent.pre.what_is_your_childs_weight_kg_merged = 
           if_else(condition = is.na(pardi.parent.pre.what_is_your_childs_weight_kg_merged),
                   
                   #Covert stone and lbs to kg
                   true = (pardi.parent.pre.what_is_your_childs_weight.2_unc*6.35029) +
                     (pardi.parent.pre.what_is_your_childs_weight.3_unc*0.453592),
                   false = NA_real_, 
                   missing = NA_real_), 
         
         #Convert lbs to kg
         pardi.parent.pre.what_is_your_childs_weight_kg_merged = 
           if_else(condition = is.na(pardi.parent.pre.what_is_your_childs_weight_kg_merged),
                   true = (pardi.parent.pre.what_is_your_childs_weight_lbs_unc*0.453592),
                   false = NA_real_, 
                   missing = NA_real_), 
         
         #kg
         pardi.parent.pre.what_is_your_childs_weight_kg_merged = 
           if_else(condition = is.na(pardi.parent.pre.what_is_your_childs_weight_kg_merged), 
                          true = pardi.parent.pre.what_is_your_childs_weight_kg_unc, 
                          false = pardi.parent.pre.what_is_your_childs_weight_kg_merged, 
                          missing = NA_real_
                   ))

arfid_dat %>% 
  descr(pardi.parent.pre.what_is_your_childs_weight_kg_merged)
```


## Clean weight in kg 
Need to consider that this is a specialist eating disorder clinic and weight may be higher and/or lower than the average population. Discussion with ARFID clinical team about plausible weights in the ARFID outpatient clinic. 

Filter ARFID ID of patient with weight of 140kg and write as excel. 
Check this value with ARFID clinical team at SLaM

```{r filter and write excel - weight}
weight <- arfid_dat %>% 
  select(ARFID_ID, 
         pardi.parent.pre.what_is_your_childs_weight_kg_merged) %>% 
  filter(pardi.parent.pre.what_is_your_childs_weight_kg_merged == 140
         )

write.xlsx(
  weight,
  file = paste0("ARFID_IDs_weight", date, ".xlsx"),
  sheetName = "Sheet1",
  col.names = TRUE,
  row.names = TRUE,
  append = FALSE,
  showNA = TRUE,
  password = NULL
)
```


+++RW: ARFID clinical team reported that this patient's weight was in fact 165kg, should I edit this?
+++CH: Yes, please, correct the value

```{r Updated weight from clinician}
arfid_dat <- arfid_dat %>%
  mutate(pardi.parent.pre.what_is_your_childs_weight_kg = 
           if_else(
             ARFID_ID == "AR21036", 
             true = 165, 
             false = pardi.parent.pre.what_is_your_childs_weight_kg_merged, 
             missing = NA_real_
             ))
```

Check this worked: 
```{r check this worked}
arfid_dat %>% 
  select(ARFID_ID, 
         pardi.parent.pre.what_is_your_childs_weight_kg) %>% 
  filter(ARFID_ID == "AR21036"
         )
```
This worked - changed patient ARFID_ID == "AR21036" from 140kg to 165kg. 

Check descriptive statistics 
```{r weight in kg descriptive}
arfid_dat %>% 
  freq(pardi.parent.pre.what_is_your_childs_weight_kg)
```

No more cleaning for weight needed. 


# Create BMI variable
Formula = kg/m2
```{r create BMI}
arfid_dat$pardi.parent.pre.current_bmi_child <- NA

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.current_bmi_child = 
  if_else(condition = is.na(pardi.parent.pre.current_bmi_child), 
         true = pardi.parent.pre.what_is_your_childs_weight_kg/
           pardi.parent.pre.what_is_your_childs_height_metres^2, 
         false = NA_real_,
         missing = NA_real_))

arfid_dat %>% 
  select(ARFID_ID,
         child.parent.pre.age_yrs_dec_unc, 
         pardi.parent.pre.current_bmi_child) 
```

## BMI z-score based on UK90 Growth reference data

For this dissertation project BMI for age z-scores will be computed using the UK90 growth data as it is a UK sample.

For children and adolescents, BMI z-scores or percentiles should be adjusted for age and sex 
And compared against growth data from a reference population

https://www.rcpch.ac.uk/resources/uk-who-growth-charts-2-18-years
https://khub.net/documents/31798783/32039025/A+simple+guide+to+classifying+body+mass+index+in+children/ced23256-6f8d-43c7-9f44-222e2beebf97?version=1.0
https://www.monicagerber.com/post/roundup-of-growth-chart-packages/

BMI for age z-score based on UK90 Growth reference data

```{r BMI for age sds - UK}
arfid_dat <- arfid_dat %>% 
  mutate(
    pardi.parent.pre.current_bmi_age_sds =
  sds(pardi.parent.pre.current_bmi_child, 
      age = child.parent.pre.age_yrs,
      sex = child.parent.pre.biological_sex_of_your_child_at_birth_binary, 
      male = "Male", 
      female = "Female", 
      ref = uk1990.ref, 
      item = "bmi", 
      type = "SDS" #for z-scores
      )
  )
```

BMI-for-age percentiles based on UK90 growth reference data
```{r BMI-for-age percentile}
arfid_dat <- arfid_dat %>% 
  mutate(
    pardi.parent.pre.bmi_percentile =
  sds(pardi.parent.pre.current_bmi_child, 
      age = child.parent.pre.age_yrs,
      sex = child.parent.pre.biological_sex_of_your_child_at_birth_binary, 
      male = "Male", 
      female = "Female", 
      ref = uk1990.ref, 
      item = "bmi", 
      type = "perc" #perc for percentile
      )
  )
   
```

Check BMI-for-age z-scores and percentiles
```{r check z-scores and percentiles}
#And check output
arfid_dat %>% 
  select(ARFID_ID,
         child.parent.pre.age_yrs,
         child.parent.pre.biological_sex_of_your_child_at_birth_binary,
         pardi.parent.pre.what_is_your_childs_height_metres,
         pardi.parent.pre.what_is_your_childs_weight_kg,
         pardi.parent.pre.current_bmi_child,
         pardi.parent.pre.current_bmi_age_sds,
         pardi.parent.pre.bmi_percentile
         )
```

Z-score descriptive (report these in dissertation)
```{r BMI z-score descriptives}
arfid_dat %>% 
  descr(pardi.parent.pre.current_bmi_age_sds)
```
The sample's mean BMI-for-age z-score is -1.23



##Diagnostic Criteria - Binary Variables 
Abscence (0) or presence (1) of the diagnostic criteria

Min and max scale 
```{r PARDI diagnostic criteria min and max scale}
pardi.dx.min.scale = 0
pardi.dx.max.scale = 1
```

diagnostic criteria vector
```{r PARDI diagnostic criteria vector}
pardi_diagnostic_criteria <- c(
  "pardi.parent.pre.pace_difficulty_gaining_difficulty_numeric_unc", 
    #failure to gain weight
    "pardi.parent.pre.child_eating_habits_led_numeric_unc", 
    #child has lost weight
    "pardi.parent.pre.health_professional_expected_told_numeric_unc", 
    #not growing as expected
    "pardi.parent.pre.health_professional_eating_habits_numeric_unc", 
    #nutritional defiency
    "pardi.parent.pre.nutrition_past_month_child_numeric_unc", 
    #nutritional oral supplement
    "pardi.parent.pre.gain_weight_child_maintain_numeric_unc", 
    #weight oral supplement
    "pardi.parent.pre.receiving_tube_feeding_child_numeric_unc",  
    #tube feeding
    "pardi.parent.pre.college_day_home_work_numeric_unc"
    #psychosocial impairment
  )

pardi_diagnostic_criteria
```

Clean diagnostic criteria variables
```{r clean diagnostic criteria variables}
arfid_dat <- arfid_dat %>%
   mutate(
     across(all_of(pardi_diagnostic_criteria),
            .fns = list(clean = ~case_when(
              . == -77 | . == -88 | . == -99 ~ .,
              . < pardi.dx.min.scale | . > pardi.dx.max.scale ~ NA_real_, 
              TRUE ~ .)))) %>%
   rename_at(
     vars(contains( "_unc_clean")),
     list(~paste0(gsub("_unc_clean", "", .))))
```



Inspect the PARDI items for diagnostic criteria
```{r inspect PARDI diagnostic criteria items}
arfid_dat %>%
  select(
    "pardi.parent.pre.pace_difficulty_gaining_difficulty_numeric", 
    #failure to gain weight
    "pardi.parent.pre.child_eating_habits_led_numeric", 
    #child has lost weight
    "pardi.parent.pre.health_professional_expected_told_numeric", 
    #not growing as expected
    "pardi.parent.pre.health_professional_eating_habits_numeric", 
    #nutritional defiency
    "pardi.parent.pre.nutrition_past_month_child_numeric", 
    #nutritional oral supplement
    "pardi.parent.pre.gain_weight_child_maintain_numeric", 
    #weight oral supplement
    "pardi.parent.pre.receiving_tube_feeding_child_numeric",  
    #tube feeding
    "pardi.parent.pre.college_day_home_work_numeric"
    )  %>%    
    #psychosocial impairment
  freq()
```
cleaned versions numeric
Need to create binary factor versions

##Create factor variable

###Failure to maintain weight
Have your child's eating habits led to difficulty maintaining a sufficient weight or, if they are growing, difficulty gaining enough weight to keep pace with their growth?
```{r difficulty maintaining weight binary variable}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.pace_difficulty_gaining_difficulty_binary = 
           recode_factor(
             pardi.parent.pre.pace_difficulty_gaining_difficulty_numeric, 
             `0` = "No difficulty maintaining weight",
             `1` = "Difficulty maintaining weight"))

arfid_dat %>% 
  freq(pardi.parent.pre.pace_difficulty_gaining_difficulty_binary)
```

##Failure to grow
```{r failure to grow binary variable}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.health_professional_expected_told_binary = 
           recode_factor(
             pardi.parent.pre.health_professional_expected_told_numeric, 
             `0` = "No slow growth",
             `1` = "Slow growth"))


arfid_dat %>% 
  freq(pardi.parent.pre.health_professional_expected_told_binary)
```


##Weight loss 
Have your child's eating habits led to them losing weight ?
```{r child has lost weight binary variable}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.child_eating_habits_led_binary = 
           recode_factor(pardi.parent.pre.child_eating_habits_led_numeric, 
             `0` = "No weight loss",
             `1` = "Child lost weight"))


arfid_dat %>% 
  freq(pardi.parent.pre.child_eating_habits_led_binary)
```

##Nutritional deficiency
Over the past month, has any health professional said that your child has a nutritional deficiency due to their eating habits ?
```{r nutritional deficiency binary variable}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.health_professional_eating_habits_binary = 
           recode_factor(pardi.parent.pre.health_professional_eating_habits_numeric, 
             `0` = "No nutritional deficiency",
             `1` = "Nutritional deficiency"))


arfid_dat %>% 
  freq(pardi.parent.pre.health_professional_eating_habits_binary)

```

##Dependence on enteral feeding or oral supplements for weight or nutrition
To create a binary variable for diagnostic criteria A3 combine information from 3 items: 
1. oral supplements for nutrition 
2. oral supplements for weight 
3. enteral feeding
```{r enteral feeding/oral supplement binary numeric}
arfid_dat <- arfid_dat %>%
  mutate(pardi.parent.pre.enteral_feeding_oral_supplement_binary_numeric =
           if_else(condition = 
                     pardi.parent.pre.nutrition_past_month_child_numeric == 1 |
                     pardi.parent.pre.gain_weight_child_maintain_numeric == 1 |
                     pardi.parent.pre.receiving_tube_feeding_child_numeric == 1,
                   true = 1,
                   false = 0,
                   missing = NA_real_))

arfid_dat %>% 
  freq(pardi.parent.pre.enteral_feeding_oral_supplement_binary_numeric)
```

recode as factor: 
```{r enteral feeding/oral supplement binary factor}
arfid_dat <- arfid_dat %>%
  mutate(pardi.parent.pre.enteral_feeding_oral_supplement_binary = 
           recode_factor(pardi.parent.pre.enteral_feeding_oral_supplement_binary_numeric, 
                         `0` = "No enteral feeding/oral supplements", 
                         `1` = "Enteral feeding or oral supplements"))

arfid_dat %>% 
  freq(pardi.parent.pre.enteral_feeding_oral_supplement_binary)
```


Psychosocial Impairment
```{r psychosocial impairment binary variable}
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.college_day_home_work_binary = 
           recode_factor(pardi.parent.pre.college_day_home_work_numeric, 
             `0` = "No psychosocial impairment",
             `1` = "Psychosocial impairment"))
  

arfid_dat %>%
  freq(pardi.parent.pre.college_day_home_work_binary)
```


## PARDI scale: 
11 items on a scale of 0 - 6. 

min and max scale
```{r PARDI min and max scale}
pardi.min.scale = 0
pardi.max.scale = 6
```

PARDI scale vector
```{r PARDI vector}
pardi_parent_pre_numeric <- c(
  "pardi.parent.pre.interactions_people_eating_difficulties_numeric_unc",
  "pardi.parent.pre.difficult_social_situations_social_numeric_unc", 
  "pardi.parent.pre.taste_variation_sensitive_past_numeric_unc", 
  "pardi.parent.pre.consistency_sensitive_past_month_numeric_unc", 
  "pardi.parent.pre.appearance_sensitive_past_month_numeric_unc", 
  "pardi.parent.pre.child_forgotten_forgotten_make_numeric_unc", 
  "pardi.parent.pre.child_appeared_lack_enjoyment_numeric_unc", 
  "pardi.parent.pre.stopped_eating_early_finished_numeric_unc", 
  "pardi.parent.pre.affected_choking_pain_type_numeric_unc", 
  "pardi.parent.pre.child_avoided_eating_situations_numeric_unc",
  "pardi.parent.pre.child_expressed_panic_physical_numeric_unc")

pardi_parent_pre_numeric
```

Clean Pardi scale 0 - 6
```{r clean PARDI scale}
arfid_dat <- arfid_dat %>%
   mutate(
     across(all_of(pardi_parent_pre_numeric),
            .fns = list(clean = ~case_when(
              . == -77 | . == -88 | . == -99 ~ .,
              . < pardi.min.scale | . > pardi.max.scale ~ NA_real_, 
              TRUE ~ .)))) %>%
   rename_at(
     vars(contains( "_unc_clean")),
     list(~paste0(gsub("_unc_clean", "", .))))
```


Create factor variables of each PARDI item which is on a scale of 0 - 6 for 
the correlation matrix and Likert plots of PARDI endorsement
```{r PARDI items factor}

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.interactions_people_eating_difficulties = 
            as.factor(pardi.parent.pre.interactions_people_eating_difficulties_numeric))

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.difficult_social_situations_social = 
            as.factor(pardi.parent.pre.difficult_social_situations_social_numeric))


arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.taste_variation_sensitive_past = 
            as.factor(pardi.parent.pre.taste_variation_sensitive_past_numeric))

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.consistency_sensitive_past_month = 
            as.factor(pardi.parent.pre.consistency_sensitive_past_month_numeric))

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.appearance_sensitive_past_month = 
            as.factor(pardi.parent.pre.appearance_sensitive_past_month_numeric))


arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.child_appeared_lack_enjoyment = 
            as.factor(pardi.parent.pre.child_appeared_lack_enjoyment_numeric))

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.child_forgotten_forgotten_make = 
            as.factor(pardi.parent.pre.child_forgotten_forgotten_make_numeric))

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.stopped_eating_early_finished = 
            as.factor(pardi.parent.pre.stopped_eating_early_finished_numeric))
         
 
arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.affected_choking_pain_type = 
            as.factor(pardi.parent.pre.affected_choking_pain_type_numeric))

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.child_avoided_eating_situations = 
            as.factor(pardi.parent.pre.child_avoided_eating_situations_numeric))

arfid_dat <- arfid_dat %>% 
  mutate(pardi.parent.pre.child_expressed_panic_physical = 
            as.factor(pardi.parent.pre.child_expressed_panic_physical_numeric))

```


# PARDI sum scores for: 
## Severity of impact
```{r psychosocial impairment severity}
arfid_dat$pardi.psychosocial_impairment_severity_numeric <- NA

arfid_dat$pardi.psychosocial_impairment_severity_numeric <- 
  rowSums(arfid_dat[c(
    "pardi.parent.pre.interactions_people_eating_difficulties_numeric",
    "pardi.parent.pre.difficult_social_situations_social_numeric")])

arfid_dat %>%
  descr(pardi.psychosocial_impairment_severity_numeric)
```


# PARDI profiles 

## Sensory avoidance of food
```{r sensory sensitivities}
arfid_dat$pardi.sensory_sensitivities_numeric <- NA

arfid_dat$pardi.sensory_sensitivities_numeric <- 
  rowSums(arfid_dat[c(
    "pardi.parent.pre.taste_variation_sensitive_past_numeric", 
    "pardi.parent.pre.consistency_sensitive_past_month_numeric",
    "pardi.parent.pre.appearance_sensitive_past_month_numeric")])

arfid_dat %>% 
  descr(pardi.sensory_sensitivities_numeric)
```


## Lack of enjoyment in eating and food
```{r lack of enjoyment}
arfid_dat$pardi.lack_of_interest_numeric <- NA

arfid_dat$pardi.lack_of_interest_numeric <- 
  rowSums(arfid_dat[c(
    "pardi.parent.pre.child_forgotten_forgotten_make_numeric", 
    "pardi.parent.pre.child_appeared_lack_enjoyment_numeric", 
    "pardi.parent.pre.stopped_eating_early_finished_numeric")])

arfid_dat %>%
  descr(pardi.lack_of_interest_numeric)
```


## Fear of aversive consequences of eating
```{r fear of aversive consequences}
arfid_dat$pardi.fear_of_aversive_consequences_numeric <- NA

arfid_dat$pardi.fear_of_aversive_consequences_numeric <- 
  rowSums(arfid_dat[c(
    "pardi.parent.pre.affected_choking_pain_type_numeric", 
    "pardi.parent.pre.child_avoided_eating_situations_numeric",
    "pardi.parent.pre.child_expressed_panic_physical_numeric")])

arfid_dat %>%
  descr(pardi.fear_of_aversive_consequences_numeric) 
```

```{r}
arfid_dat %>% 
  colnames()
```


#Save merged dataset with cleaned demographic and PARDI data:
ARFID and ASD diagnosis 
Patient sex and age
PARDI height and weight 
PARDI diagnostic criteria 
PARDI impairment severity 
PARDI profiles

```{r save data as rds}
saveRDS(
  arfid_dat, 
  file = paste0("../data/ARFID_data_dem_PARDI_cleaned", date, ".rds")
)
```



