---
title: "Correlation Matrix"
author: "Rosie Watts"
date: "18/08/2021"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

Research question 1: Examine how ARFID symptoms correlate with one another. 
Research question 2: Examine how anxiety correlate with symptoms of ARFID. 

To answer the first two research questions we will use a heterogeneous correlation matrix to test the correlations of both continuous and categorical data.

# Set up R Markdown
```{r setup, include=FALSE, out.width='100%'}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment 
```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Set current date 
```{r current date}
date <- Sys.Date()
```

Install necessary packages
```{r install packages, eval=FALSE, include=FALSE}
#install.packages("knitr")
#install.packages("summarytools")
#install.packages("skimr")
#install.packages("polycor")
#install.packages("corrplot")
#install.packages("corrr")
#install.packages("broom")
#install.packages("poolr")
#install.packages("magrittr")
#install.packages("tidyverse")
```

Load packages
```{r load packages}
library(knitr)
library(summarytools)
library(skimr)
library(polycor)
library(corrplot)
#library(corrr)
library(rstatix)
library(broom)
library(poolr)
#library(magrittr)
library(xlsx)
library(tidyverse)
```

Read in clean data
```{r read in clean data}
arfid_dat <- readRDS(file = "../Data/arfid_data_clean2021-08-18.rds")
```

#Inspect the data

```{r skim}
arfid_dat %>% 
  skim()
```



#Hetcor matrix function
Select variables and run hetcor using pairwise complete observations
And print arfid.het.cor =
1. Correlation coefficients and type of correlations 
2. Standard errors and number of pairwise complete observations
3. p-values
```{r select variables and run hetcor}
arfid.het.cor <- arfid_dat %>% 
  select(
    #BMI for age z-score (continuous)
    "pardi.parent.pre.current_bmi_age_sds",
    
    #Nutritional deficiencies (binary)
    "pardi.parent.pre.health_professional_eating_habits_binary",       
    
    #ARFID symptoms (factor)
    "pardi.parent.pre.interactions_people_eating_difficulties", 
    #interactions with others
    "pardi.parent.pre.difficult_social_situations_social",      
    #social situations
    "pardi.parent.pre.taste_variation_sensitive_past",          
    #sensory sensitivity - taste
    "pardi.parent.pre.consistency_sensitive_past_month",        
    #sensory sensitivity - texture
    "pardi.parent.pre.appearance_sensitive_past_month",         
    #sensory sensitivity - appearance 
    "pardi.parent.pre.child_forgotten_forgotten_make",          
    #forgotten to eat
    "pardi.parent.pre.child_appeared_lack_enjoyment",    
    #lacked enjoyment in food
    "pardi.parent.pre.stopped_eating_early_finished",     
    #full/stopped eating early
    "pardi.parent.pre.affected_choking_pain_type",     
    #afraid something bad might happen
    "pardi.parent.pre.child_avoided_eating_situations",         
    #avoided eating due to such worries
    "pardi.parent.pre.child_expressed_panic_physical",       
    #physical feelings of panic and anxiety
    
    #Anxety disorder z-scores (continuous)
    "social_phobia_zscore",                                                
    "generalised_anxiety_zscore",                                            
    "separation_anxiety_zscore",                                              
    "panic_disorder_zscore", 
    "CV.specific_phobia_zscore", 
    "CV.agoraphobia_zscore" 
    
    ) %>% 
  
  as.data.frame() %>%
  
  hetcor(use = "pairwise.complete.obs"
         #ML = T 
  )

arfid.het.cor
```


Save as a correlation matrix
```{r correlation as matrix}
arfid.het.cor.matrix <- as.matrix(arfid.het.cor)
```

Save p-values from the correlation matrix as an object 
```{r p values matrix}
p.values.matrix <- as.matrix(arfid.het.cor$tests, round(4))
```


##Indpendent traits
Calculate the number of independent traits within the correlation matrix to adjust for multiple testing: 

https://www.rdocumentation.org/packages/poolr/versions/1.0-0/topics/meff 
Methods: "nyholt", "liji", "gao", or "galwey"

Independent tests using 'galwey' methods = 13 
Bonferroni adjustment = 0.05/13 = 0.004

```{r independent traits}
meff(arfid.het.cor.matrix, 
     method = "galwey")
```

#Plot the Heterogeneous correlation matrix
Save column and row names for correlation matrix
```{r col and row names}
colnames(arfid.het.cor.matrix) <- 
  c(
    "BMI for age z-score",
    "nutritional deficiency", 
    
    
    "difficulty: interactions with others",
    "difficulty: social situations",
    "sensory sensitivity: taste",
    "sensory sensitivity: texture",
    "sensory sensitivity: appearance",
    "forgotten to eat",
    "lacked enjoyment in food", 
    "stopped eating early", 
    "afraid something bad might happen",
    "avoided eating due to such worries", 
    "physical feelings of panic and anxiety",
    
    #"ASD",
    
    "social anxiety z-score", 
    "generalised anxiety z-score", 
    "separation anxiety z-score", 
    "panic disorder z-score", 
    "specific phobia z-score", 
    "agoraphobia z-score"
    )


rownames(arfid.het.cor.matrix) <- 
  c(
    "BMI for age z-score",
    "nutritional deficiency", 
   
    
    "difficulty: interactions with others",
    "difficulty: social situations",
    "sensory sensitivity: taste",
    "sensory sensitivity: texture",
    "sensory sensitivity: appearance",
    "forgotten to eat",
    "lacked enjoyment in food", 
    "stopped eating early", 
    "afraid something bad might happen",
    "avoided eating due to such worries", 
    "physical feelings of panic and anxiety",
    
    #"ASD",
    
    
    "social anxiety z-score", 
    "generalised anxiety z-score", 
    "separation anxiety z-score", 
    "panic disorder z-score", 
    "specific phobia z-score", 
    "agoraphobia z-score"
    )
```

Use corrplot to plot matrix
(Hash out saving the plot for now)
```{r het corrplot}
#png('arfid.het.corrplot.png', res = 300, width=2800, height=2800)

arfid.het.cor.matrix %>%
  corrplot(method = "color", 
           type = "lower",             #shows lower half of correlation matrix
           diag = TRUE,                #remove diagonal correlation
           #order = "hclust",          #order of vars: original, AOE, hclust
           #hclust.method = 
           #addrect = 4,               #no. of rectangles drawn - hclust
           addCoef.col = "black",      #add correlation coefficients
           addgrid.col = "white",      #add colour of grid lines
           number.cex = .55,           #size of correlation coefficients
           number.font = 1,            #font of correlation coefficients
           tl.col = "black",           #black labels
           tl.srt = 45,                #rotate labels
           tl.cex = .75,               #font size of labels
           cl.cex = 0.75,
           
           #Combine with p-values 
           p.mat = p.values.matrix,      #matrix with p-levels 
           sig.level = 0.004,          #adjusted significance level (edit)
           insig = "blank", 
          
          #Reverse colour scheme
           col=colorRampPalette(c("dodgerblue4",
                                  "white",
                                  "firebrick4"))(200))
           
#dev.off()
```

#Create a table of the correlation matrix

```{r correlation matrix data frame}
Correlation_Matrix_data_frame_table <-
as.data.frame(as.table(arfid.het.cor.matrix))

Correlation_Matrix_data_frame_table <- 
  Correlation_Matrix_data_frame_table %>% 
  rename("Variable 1" = "Var1", 
         "Variable 2" = "Var2", 
         "r" = "Freq") 

Correlation_Matrix_data_frame_table
```



#Number of pairwise complete obs in each correlation 
Include this as an appendix
```{r number of pairwise complete obs in each correlation}
ARFID_correlation_matrix_number = as.data.frame(
  arfid.het.cor$n)
```

Rename variable names 
```{r rename column names}
ARFID_correlation_matrix_number <- ARFID_correlation_matrix_number %>% 
  rename(
    "BMI for age z-score" = "V1",
    "nutritional deficiency" = "V2", 
  
    "difficulty: interactions with others" = "V3",
    "difficulty: social situations" = "V4",
    "sensory sensitivity: taste" = "V5",
    "sensory sensitivity: texture" = "V6",
    "sensory sensitivity: appearance" = "V7",
    "forgotten to eat" = "V8",
    "lacked enjoyment in food" = "V9", 
    "stopped eating early" = "V10", 
    "afraid something bad might happen" = "V11",
    "avoided eating due to such worries" = "V12", 
    "physical feelings of panic and anxiety" = "V13", 
    
    "social anxiety" = "V14", 
    "generalised anxiety" = "V15", 
    "separation anxiety" = "V16", 
    "panic disorder" = "V17", 
    "specific phobia" = "V18", 
    "agoraphobia" = "V19"
  )
```

Mutate column with row names
```{r new column with row names}
ARFID_correlation_matrix_number <- ARFID_correlation_matrix_number %>% 
  mutate(Rows = 
           rownames(arfid.het.cor.matrix))

ARFID_correlation_matrix_number
```

Write as an excel to format table and attach as an appendix
```{r save as excel}
write.xlsx(
  ARFID_correlation_matrix_number,
  file = "ARFID_correlation_matrix_number.xlsx",
  sheetName = "Sheet2",
  col.names = TRUE,
  row.names = TRUE,
  append = FALSE,
  showNA = TRUE,
  password = NULL
)
```


#Visualise the relationship of variables
Check some of the correlations from the heterogeneous correlation matrix by visualising the relationship between the variables 

##ARFID drivers

###Sensory sensitivities 
taste and texture 
r = 0.81, p = 0.07
```{r visualise: sensory sensitivity to taste and texture}
sensory_1 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.taste_variation_sensitive_past_numeric, 
             y = pardi.parent.pre.consistency_sensitive_past_month_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Sensory sensitivty: taste") + 
  ylab("Sensory sensitivity: texture") + 
  theme_minimal()

sensory_1
```

taste and appearance 
r = 0.65  , p = 0.14
```{r visualise: sensory sensitivity to taste and appearance}
sensory_2 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.taste_variation_sensitive_past_numeric, 
             y = pardi.parent.pre.appearance_sensitive_past_month_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Sensory sensitivty: taste") + 
  ylab("Sensory sensitivity: appearance") + 
  theme_minimal()

sensory_2
```

texture and appearance 
r = 0.65  , p = 0.007
```{r visualise: sensory sensitivity to texture and appearance}
sensory_3 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.consistency_sensitive_past_month_numeric, 
             y = pardi.parent.pre.appearance_sensitive_past_month_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Sensory sensitivty: texture") + 
  ylab("Sensory sensitivity: appearance") + 
  theme_minimal()

sensory_3
```

###Lack of interest
forgotten to eat and lack enjoyment 
r = 0.66  , p = 0.89
```{r visualise: forgotten to eat and lack enjoyment }
interest_1 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.child_forgotten_forgotten_make_numeric, 
             y = pardi.parent.pre.child_appeared_lack_enjoyment_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Lack of interest: forgotten to eat") + 
  ylab("Lack of interest: lacked enjoyment") + 
  theme_minimal()

interest_1
```

forgotten to eat and stopped eating early
r = 0.58  , p = 0.30
```{r visualise: forgotten to eat and stopped eating early}
interest_2 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.child_forgotten_forgotten_make_numeric, 
             y = pardi.parent.pre.stopped_eating_early_finished_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Lack of interest: forgotten to eat") + 
  ylab("Lack of interest: stopped eating early") + 
  theme_minimal()

interest_2
```

Stopped eating early and lack enjoyment 
r = 0.57  , p = 0.33
```{r visualise: lack enjoyment and stopped eating early}
interest_3 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.child_appeared_lack_enjoyment_numeric, 
             y = pardi.parent.pre.stopped_eating_early_finished_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Lack of interest: lacked enjoyment") + 
  ylab("Lack of interest: stopped eating early") + 
  theme_minimal()

interest_3
```

###Fear of aversive consequences
Afraid something bad might happen and avoided eating due to worries
r = 0.88  , p = 0.00004
```{r visualise: afraid and avoided}
fear_1 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.affected_choking_pain_type_numeric, 
             y = pardi.parent.pre.child_avoided_eating_situations_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Fear of aversive consequences: afraid something bad might happen") + 
  ylab("Fear of aversive consequences: avoided eating due to worries") + 
  theme_minimal()

fear_1
```

Afraid something bad might happen and physical feelings of panic and anxiety
r = 0.79  , p = 0.04 
```{r visualise: afraid and physical feelings of panic and anxiety}
fear_2 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.affected_choking_pain_type_numeric, 
             y = pardi.parent.pre.child_expressed_panic_physical_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Fear of aversive consequences: afraid something bad might happen") + 
  ylab("Fear of aversive consequences: physical feelings of panic and anxiety") + 
  theme_minimal()

fear_2
```

Avoided eating due to worries and physical feelings of panic and anxiety
r = 0.75  , p = 0.04
```{r visualise: avoided and physical feelings of panic and anxiety}
fear_3 <- arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.child_avoided_eating_situations_numeric, 
             y = pardi.parent.pre.child_expressed_panic_physical_numeric)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Fear of aversive consequences: avoided eating due to worries") + 
  ylab("Fear of aversive consequences: physical feelings of panic and anxiety") + 
  theme_minimal()

fear_3
```

####Format and save these plots for appendices
Could discuss the relationship between the three items in each ARFID driver in the discussion and attach these plots as appendices. 
Format with cowplot:
```{r Sensory sensitivities cowplot}
sensory_correlations <- 
  cowplot::plot_grid(sensory_1, sensory_2, sensory_3,
                     labels = c("A", 
                                "B", 
                                "C"), 
                     label_size = 12, 
                     scale = 0.9,
                     nrow = 1) 

sensory_correlations
```

```{r ggsave sensory}
ggsave(
  filename = paste0("sensory_correlations", date, ".pdf"), 
  path = "../plots/",
  plot = sensory_correlations,
  device = "pdf",
  scale = 1,
  width = 14,
  height = 5,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```

```{r lack of interest cowplot}
interest_correlations <- 
  cowplot::plot_grid(interest_1, interest_2, interest_3,
                     labels = c("A", 
                                "B", 
                                "C"), 
                     label_size = 12, 
                     scale = 0.9,
                     nrow = 1) 

interest_correlations
```

```{r ggsave interest}
ggsave(
  filename = paste0("interest_correlations", date, ".pdf"), 
  path = "../plots/",
  plot = interest_correlations,
  device = "pdf",
  scale = 1,
  width = 14,
  height = 5,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```

```{r fear cowplot}
fear_correlations <- 
  cowplot::plot_grid(fear_1, fear_2, fear_3,
                     labels = c("A", 
                                "B", 
                                "C"), 
                     label_size = 12, 
                     scale = 0.9,
                     nrow = 1) 

fear_correlations
```

```{r ggsave fear}
ggsave(
  filename = paste0("fear_correlations", date, ".pdf"), 
  path = "../plots/",
  plot = fear_correlations,
  device = "pdf",
  scale = 1,
  width = 15,
  height = 6,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```


##Anxiety and ARFID drivers 
- pick a couple of correlations to visually inspect

Generalised anxiety and sensory sensitivity to appearance
r = 0.31, p = 5.63E-08
```{r visualise: Generalised anxiety and sensory sensitivity to appearance}
arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.appearance_sensitive_past_month_numeric, 
             y = generalised_anxiety_zscore)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Sensory sensitivities: appearance") + 
  ylab("Generalised anxiety z-score")
```

Separation anxiety and stopped eating early
r = 0.13, p = 1.21E-05
```{r visualise: separation anxiety and stopped eating early}
arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.stopped_eating_early_finished_numeric, 
             y = separation_anxiety_zscore)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Lack of interest: stopped eating early") + 
  ylab("Separation anxiety z-score")
```

panic disorder and physical feelings of panic and anxiety 
r = 0.43, p = 4.12E-13
```{r visualise: Panic disorder and fear of aversive consequences}
arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.child_expressed_panic_physical_numeric, 
             y = panic_disorder_zscore)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Fear of aversive consequences: physical feelings of panic and anxiety") + 
  ylab("Panic disorder z-score")
```

##ARFID drivers and BMI-for-age z-scores
- pick a couple of correlations to visually inspect

BMI and sensory sensitivity to taste
r = 0.40, p = 0.0004
```{r visualise: BMI and sensory sensitivity to taste}
arfid_dat %>% 
  ggplot(aes(x = pardi.parent.pre.taste_variation_sensitive_past_numeric, 
             y = pardi.parent.pre.current_bmi_age_sds)) + 
  geom_point() + 
  geom_jitter(position = 
                position_jitter(height = 0.2, width = 0.2)) + 
  xlab("Sensory sensitivities: taste") + 
  ylab("BMI-for-age z-scores")
```



#Check the individual correlations between items 
Calculuate individual correlation between a few variables to check these against the hetcor matrix

##biserial 
polserial() from the polychor package with 
x = continuous 
y = factor with two levels (binary)
```{r biserial correlations}
polyserial(x = arfid_dat$pardi.parent.pre.current_bmi_age_sds, 
           y = arfid_dat$pardi.parent.pre.health_professional_eating_habits_binary, 
           std.err = TRUE)
```
This correlation coefficient and p-value corresponds with the hetcor matrix 


##Polychoric 
binary factor and categorical factor 
```{r polychoric with binary}
polychor(x = arfid_dat$pardi.parent.pre.taste_variation_sensitive_past,
         y = arfid_dat$pardi.parent.pre.health_professional_eating_habits_binary,
         std.err = TRUE) 
```
This correlation coefficient and p-value corresponds with the hetcor matrix 


##polychoric 
categorical and categorical (ARFID symptoms)
```{r polychoric correlations}

#polycor package

polychor(x = arfid_dat$pardi.parent.pre.consistency_sensitive_past_month, 
        y = arfid_dat$pardi.parent.pre.taste_variation_sensitive_past, 
         std.err = TRUE) 


polychor(x = arfid_dat$pardi.parent.pre.appearance_sensitive_past_month, 
        y = arfid_dat$pardi.parent.pre.child_appeared_lack_enjoyment, 
         std.err = TRUE) 


polychor(x = arfid_dat$pardi.parent.pre.affected_choking_pain_type,
         y = arfid_dat$pardi.parent.pre.child_avoided_eating_situations, 
         std.err = TRUE)


polychor(x = arfid_dat$pardi.parent.pre.consistency_sensitive_past_month,
         y = arfid_dat$pardi.parent.pre.child_forgotten_forgotten_make, 
         std.err = TRUE)


polychor(x = arfid_dat$pardi.parent.pre.taste_variation_sensitive_past,
         y = arfid_dat$pardi.parent.pre.child_appeared_lack_enjoyment, 
         std.err = TRUE)

```
These correlation coefficients and p-values are the same as the one created by hetcor()


##Polyserial 
categorical and continous
```{r polyserial correlations}

#polycor package 

polyserial(x = arfid_dat$pardi.parent.pre.current_bmi_age_sds,
           y = arfid_dat$pardi.parent.pre.consistency_sensitive_past_month, 
           std.err = TRUE) 

polyserial(x = arfid_dat$generalised_anxiety_zscore,
           y = arfid_dat$pardi.parent.pre.appearance_sensitive_past_month_numeric, 
           std.err = TRUE) 

```
These correlation coefficients nd p-values are the same as the one created by hetcor()


continuous
```{r pearson correlation}
arfid_dat %>% 
  select(generalised_anxiety_zscore,
         panic_disorder_zscore) %>% 
  cor(use = "pairwise.complete.obs")
```
This correlation coefficients is the same as the one created by hetcor()
