---
title: "ARFID Sex Differences"
author: "Rosie Watts"
date: "12/07/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

#Set up R Markdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width='100%', out.height='100%')
```

Clear Global Environment 
```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Set current date 
```{r current date}
date <- Sys.Date()
```

Install necessary packages
```{r install packages}
#install.packages("knitr")
#install.packages("summarytools")
#install.packages("skimr")
#install.packages("psych")
#install.packages("gt")
#install.packages("sjPlot")
#install.packages("sjmisc")
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("gtsummary")
#install.packages("rcompanion")
#install.packages("patchwork")
#install.packages("car")
#install.packages("pscl")
#install.packages("ggfortify")
#install.packages("broom")
#install.packages("MASS")
#install.packaes("tidyverse")
```

Load necessary packages 
```{r load packages}
library(knitr)
library(summarytools)
library(skimr)
library(psych)
library(sjPlot)
library(likert)
library(ggplot2)
library(gtsummary)
library(patchwork)
library(data.table)
library(rcompanion)
library(car)
library(ggfortify)
library(broom) 
library(boot)
library(pscl)
library(cowplot)
library(tidyverse)
```

Read in data
```{r read in raw_data}
arfid_dat <- readRDS(file = "../data/arfid_data_clean2021-08-18.rds")
```

#Inspect the dataset
```{r skim}
arfid_dat %>% 
  skim()
```


#Visually Inspect the distribution of PARDI Profiles data 
Outcome variables in regression

##Sensory sensitivity
Histrogram
```{r sensory sensitivity profile histogram}
h1 <- arfid_dat %>% 
  ggplot(aes(x = pardi.sensory_sensitivities_numeric, 
             fill = child.parent.pre.biological_sex_of_your_child_at_birth_binary)) +
  geom_histogram(position = position_dodge(preserve = "single")) + 
  labs(x = "PARDI-AR-Q score", 
       y = "Count", 
       fill = "Patient's sex") +
  scale_fill_manual(values=c("#1920FA",
                             "#FACE19")) +
  theme_minimal()

h1
```

Density plot
```{r sensory sensitivity profile density plot}
d1 <- arfid_dat %>% 
  ggplot(aes(x = pardi.sensory_sensitivities_numeric)) +
  geom_density() + 
  labs(x = "PARDI profile score: Avoidance based on sensory sensitivities", 
       y = "Density") +
  theme_minimal()

d1
```

Check the skewness
```{r sensory skewness}
arfid_dat %>% 
  summarytools::descr(pardi.sensory_sensitivities_numeric)
```

Sensory sensitivities driver outcome variable is negatively skewed

##Lack of interest
Histrogram
```{r lack interest profile histogram}
h2 <- arfid_dat %>% 
  ggplot(aes(
    x = pardi.lack_of_interest_numeric,
    fill = child.parent.pre.biological_sex_of_your_child_at_birth_binary)) +
  geom_histogram(position = position_dodge(preserve = "single")) + 
  labs(x = "PARDI-AR-Q score", 
       y = "Count", 
       fill = "Patient's sex") +
  scale_fill_manual(values=c("#1920FA",
                             "#FACE19")) +
  theme_minimal()

h2
```

Density plot
```{r lack interest profile density plot}
d2 <- arfid_dat %>% 
  ggplot(aes(x = pardi.lack_of_interest_numeric)) +
  geom_density() + 
  labs(x = "PARDI profile score: Lack of interest in eating and food", 
       y = "Density") +
  theme_minimal()

d2
```

```{r interest skewness}
arfid_dat %>% 
  summarytools::descr(pardi.lack_of_interest_numeric)
```
Lack of interest driver outcome variable is negatively skewed


##Fear of aversive consequences
Histogram plot
```{r fear of aversive consequences histogram}
h3 <- arfid_dat %>% 
  ggplot(
    aes(x = pardi.fear_of_aversive_consequences_numeric,
        fill = child.parent.pre.biological_sex_of_your_child_at_birth_binary)) +
  geom_histogram(position = position_dodge(preserve = "single")) + 
  labs(x = "PARDI-AR-Q score", 
       y = "Count", 
       fill = "Patient's sex") +
  scale_fill_manual(values=c("#1920FA",
                             "#FACE19")) +
  theme_minimal()

h3
```

Density plot
```{r fear of aversive consequences density plot}
d3 <- arfid_dat %>% 
  ggplot(aes(x = pardi.fear_of_aversive_consequences_numeric)) +
  geom_density() + 
  labs(x = "PARDI profile score: Fear of aversive consequences of eating", 
       y = "Density") +
  theme_minimal()

d3
```

Check the skewness
```{r fear skewness}
arfid_dat %>% 
  summarytools::descr(pardi.fear_of_aversive_consequences_numeric)
```

Fear of aversive consequences driver outcome variable has a zero-inflated distribution



##Correlations
Inspect the correlations amongst the three PARDI profile scores
```{r Sensory and interest correlation}
arfid_dat %>% 
  select(pardi.sensory_sensitivities_numeric, 
         pardi.lack_of_interest_numeric) %>% 
  cor(use = "pairwise.complete.obs")
```

```{r sensory and fear correlation}
arfid_dat %>% 
  select(pardi.sensory_sensitivities_numeric, 
         pardi.fear_of_aversive_consequences_numeric) %>% 
  cor(use = "pairwise.complete.obs")
```

```{r fear and interest correlation}
arfid_dat %>% 
  select(pardi.fear_of_aversive_consequences_numeric, 
         pardi.lack_of_interest_numeric) %>% 
  cor(use = "pairwise.complete.obs")
```



#Likert plot for endorsement of PARDI items plotted by sex

Plot responses on PARDI-AR-Q parent 4+ for male and female patients separately

##Male
Filter by male participants and select variables to plot
```{r filter by male and select variables}
arfid_dat_likert_male <- arfid_dat %>% 
  
  filter(child.parent.pre.biological_sex_of_your_child_at_birth_binary ==
           "Male") %>%
  
  select(
    pardi.parent.pre.interactions_people_eating_difficulties,
    pardi.parent.pre.difficult_social_situations_social,
    pardi.parent.pre.taste_variation_sensitive_past,
    pardi.parent.pre.consistency_sensitive_past_month,
    pardi.parent.pre.appearance_sensitive_past_month,
    pardi.parent.pre.child_forgotten_forgotten_make,
    pardi.parent.pre.child_appeared_lack_enjoyment,
    pardi.parent.pre.stopped_eating_early_finished,
    pardi.parent.pre.affected_choking_pain_type,
    pardi.parent.pre.child_avoided_eating_situations,
    pardi.parent.pre.child_expressed_panic_physical) %>% 
  
    rename(
    "Difficulties: interactions with others" =
    pardi.parent.pre.interactions_people_eating_difficulties,
    "Difficulty: social situations" =
    pardi.parent.pre.difficult_social_situations_social,
    "Sensory sensitivity: taste" =
    pardi.parent.pre.taste_variation_sensitive_past,
    "Sensory sensitivity: texture" =
    pardi.parent.pre.consistency_sensitive_past_month,
    "Sensory sensitivity: appearance" =
    pardi.parent.pre.appearance_sensitive_past_month,
    "Forgotten to eat" = 
    pardi.parent.pre.child_forgotten_forgotten_make,
    "Lacked enjoyment in food" = 
    pardi.parent.pre.child_appeared_lack_enjoyment,
    "Stopped eating early" = 
    pardi.parent.pre.stopped_eating_early_finished,
    "Afraid something bad might happen" = 
    pardi.parent.pre.affected_choking_pain_type,
    "Avoided eating due to such worries" = 
    pardi.parent.pre.child_avoided_eating_situations,
    "Physical feelings of panic and anxiety" = 
    pardi.parent.pre.child_expressed_panic_physical)

arfid_dat_likert_male
```

Format Likert data
```{r format male likert data}
male_likert_data <- likert(arfid_dat_likert_male)
```

Plot with likert package
```{r male likert plot }
male.likert.plot <- 
  likert.bar.plot(male_likert_data, 
                  colors = 
                  c("#fef0d9", 
                    "#fdd49e", 
                    "#fdbb84",
                    "#fc8d59",
                    "#ef6548",
                    "#d7301f",
                    "#990000"),
                  plot.percent.neutral = FALSE,
                  text.color = "black",
                  text.size = 3,
                  ordered = FALSE, 
                  group.order = c(
                    "Difficulties: interactions with others", 
                    "Difficulty: social situations",
                    "Sensory sensitivity: taste",
                    "Sensory sensitivity: texture", 
                    "Sensory sensitivity: appearance", 
                    "Forgotten to eat", 
                    "Lacked enjoyment in food", 
                    "Stopped eating early", 
                    "Afraid something bad might happen", 
                    "Avoided eating due to such worries", 
                    "Physical feelings of panic and anxiety")
                  ) + 
  labs(y = "Endorsement (%)", 
       x = "PARDI-AR-Q item", 
       title = "Male", 
       subtitle = "n = 49") +
  theme_minimal() 


male.likert.plot$layers[[1]]$geom_params$width = 0.7
male.likert.plot$layers[[2]]$geom_params$width = 0.7
male.likert.plot$layers[[3]]$geom_params$width = 0.7
male.likert.plot$layers[[4]]$geom_params$width = 0.7
male.likert.plot$layers[[5]]$geom_params$width = 0.7


male.likert.plot
```

check this worked by checking frequencies against likert plot 
```{r check frequency}
arfid_dat_likert_male %>% 
  freq
```
Yes this works! 
Level 0 ,1, 2 percentage is reported on the left
Level 3 percentage is dropped 
Level 4, 5, 6 percentage is reported on the right


##Female
Filter by female and select variables to plot
```{r filter by female and select variables}
arfid_dat_likert_female <- arfid_dat %>% 
  
  filter(child.parent.pre.biological_sex_of_your_child_at_birth_binary ==
           "Female") %>%
  
  select(
    pardi.parent.pre.interactions_people_eating_difficulties,
    pardi.parent.pre.difficult_social_situations_social,
    pardi.parent.pre.taste_variation_sensitive_past,
    pardi.parent.pre.consistency_sensitive_past_month,
    pardi.parent.pre.appearance_sensitive_past_month,
    pardi.parent.pre.child_forgotten_forgotten_make,
    pardi.parent.pre.child_appeared_lack_enjoyment,
    pardi.parent.pre.stopped_eating_early_finished,
    pardi.parent.pre.affected_choking_pain_type,
    pardi.parent.pre.child_avoided_eating_situations,
    pardi.parent.pre.child_expressed_panic_physical) %>% 
  
    rename(
    "Difficulties: interactions with others" =
    pardi.parent.pre.interactions_people_eating_difficulties,
    "Difficulty: social situations" =
    pardi.parent.pre.difficult_social_situations_social,
    "Sensory sensitivity: taste" =
    pardi.parent.pre.taste_variation_sensitive_past,
    "Sensory sensitivity: texture" =
    pardi.parent.pre.consistency_sensitive_past_month,
    "Sensory sensitivity: appearance" =
    pardi.parent.pre.appearance_sensitive_past_month,
    "Forgotten to eat" = 
    pardi.parent.pre.child_forgotten_forgotten_make,
    "Lacked enjoyment in food" = 
    pardi.parent.pre.child_appeared_lack_enjoyment,
    "Stopped eating early" = 
    pardi.parent.pre.stopped_eating_early_finished,
    "Afraid something bad might happen" = 
    pardi.parent.pre.affected_choking_pain_type,
    "Avoided eating due to such worries" = 
    pardi.parent.pre.child_avoided_eating_situations,
    "Physical feelings of panic and anxiety" = 
    pardi.parent.pre.child_expressed_panic_physical)
  

arfid_dat_likert_female
```

Format Likert data
```{r format female likert data}
female_likert_data <- likert(arfid_dat_likert_female)
```

Plot with Likert package
```{r female likert plot }
female.likert.plot <- 
  likert.bar.plot(female_likert_data, 
                  colors = 
                  c("#fef0d9", 
                    "#fdd49e", 
                    "#fdbb84",
                    "#fc8d59",
                    "#ef6548",
                    "#d7301f",
                    "#990000"),
                  plot.percent.neutral = FALSE,
                  text.color = "black",
                  text.size = 3,
                  ordered = FALSE, 
                  group.order = c(
                    "Difficulties: interactions with others", 
                    "Difficulty: social situations",
                    "Sensory sensitivity: taste",
                    "Sensory sensitivity: texture", 
                    "Sensory sensitivity: appearance", 
                    "Forgotten to eat", 
                    "Lacked enjoyment in food", 
                    "Stopped eating early", 
                    "Afraid something bad might happen", 
                    "Avoided eating due to such worries", 
                    "Physical feelings of panic and anxiety")
                  ) + 
  labs(y = "Endorsement (%)", 
       x = "PARDI-AR-Q item", 
       title = "Female", 
       subtitle = "n = 60") +
  theme_minimal() 


female.likert.plot$layers[[1]]$geom_params$width = 0.7
female.likert.plot$layers[[2]]$geom_params$width = 0.7
female.likert.plot$layers[[3]]$geom_params$width = 0.7
female.likert.plot$layers[[4]]$geom_params$width = 0.7
female.likert.plot$layers[[5]]$geom_params$width = 0.7


female.likert.plot
```


##Male and Female 

Format with patchwork so that the two likert plots are side by side. 
Drop Y label from one 
Share legend
```{r patchwork landscape}
sex_likert_landscape <- male.likert.plot + female.likert.plot 

# Remove title from second subplot
sex_likert_landscape[[2]] = sex_likert_landscape[[2]] + 
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.title.y = element_blank())


sex_likert_landscape <- sex_likert_landscape +  plot_layout(guides = "collect") 

sex_likert_landscape
```


```{r patchwork portrait}
sex_likert_portrait <- male.likert.plot / female.likert.plot 

sex_likert_portrait <- sex_likert_portrait +  plot_layout(guides = "collect") 

sex_likert_portrait
```


Save Likert plot
```{r ggsave likert plot landscape}
ggsave(
  filename = paste0("likert_plot_sex_landscape", date, ".pdf"), 
  path = "../plots/",
  plot = sex_likert_landscape,
  device = "pdf",
  scale = 1,
  width = 15,
  height = 6,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```

```{r ggsave likert plot portrait}
ggsave(
  filename = paste0("likert_plot_sex_portrait", date, ".pdf"), 
  path = "../plots/",
  plot = sex_likert_portrait,
  device = "pdf",
  scale = 1,
  width = 9,
  height = 10,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```


#Regressions 

Will be computed to examine the effect of sex on the PARDI profile scores, whilst controlling for the patient's age. 
1. Sensory sensitivity profile (0 - 18)
2. Lack of interest profile (0 - 18)
3. Fear of aversive consequences profile (0 - 18)

Sex = 
"Male",
"Female"

```{r select variables}
regression_sex_arfid_dat <- arfid_dat %>% 
  select(pardi.sensory_sensitivities_numeric,
         pardi.lack_of_interest_numeric, 
         pardi.fear_of_aversive_consequences_numeric,
         patients_biological_sex =
           child.parent.pre.biological_sex_of_your_child_at_birth_binary,
         child.parent.pre.age_yrs) 
```


##Sensory sensitivity driver 
###Linear regression and plots

Run linear regression
However, due to the distribution of the outcome variable we will run and report negative bionomial regressions
```{r sensory lm}
m1 <- regression_sex_arfid_dat %>% 
  lm(formula = pardi.sensory_sensitivities_numeric ~ 
       patients_biological_sex + 
       child.parent.pre.age_yrs)

summary(m1)
```

Format in tidy table
```{r sensory tidy ouput}
sensory_table <- m1 %>%
  tidy() %>%
  mutate(
    Variable =
  recode_factor(
    term,
    "patients_biological_sexFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
  )
  ) %>%
  select(
    Variable,
    Estimate = estimate,
    SE = std.error,
    t_value = statistic,
    p_value = p.value
  )
  

kable(sensory_table)
```

Box plot of relationship between sensory sensitivities and patient's sex:
Format without legend (as going to format with multiple other plots)
```{r sensory boxplot}
g1 <- regression_sex_arfid_dat %>%
  drop_na(patients_biological_sex) %>%
  drop_na(pardi.sensory_sensitivities_numeric) %>%

  ggplot(aes(x = patients_biological_sex,
             y = pardi.sensory_sensitivities_numeric, 
             fill = patients_biological_sex)) +
  geom_boxplot(
    show.legend = FALSE) + 
  xlab("Patient's sex") + 
  ylab("PARDI-AR-Q score") + 
  labs(fill = "Patient's Sex") + 
  scale_fill_manual(values=c("#1920FA",
                             "#FACE19")) +
  theme_minimal()

g1 
```

Check lm assumptions
Multicollinearity 
```{r multicollinearity}
vif(m1)
```

Diagnostic plots

http://www.sthda.com/english/articles/39-regression-model-diagnostics/161-linear-regression-assumptions-and-diagnostics-in-r-essentials/

```{r sensory diagnostic plots}
plot(m1)
autoplot(m1)
```


###Negative Binomial Regression: 
Due to the distribution of the response variable, we will also compute a negative binomial regression for ARFID profile and compare the output. 
```{r sensory negative binomial regression}
m1nb <- 
  MASS::glm.nb(pardi.sensory_sensitivities_numeric ~ 
                 patients_biological_sex + 
                 child.parent.pre.age_yrs, 
               data = regression_sex_arfid_dat
               )

summary(m1nb)
```

Exponetiate coefficient to report output
```{r sensory NB exp}
m1nb$family$linkinv(coef(m1nb))
```

Exponentiated coefficient as a percentage
```{r sensory NB as percentage}
round((m1nb$family$linkinv(coef(m1nb))-1)*100)
```

Check r2 nagelkerke (pseudo r2)
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r sensory r2 nagelkerke}
nagelkerke(m1nb)
```

Create tidy table output: 
+++RW: exponentiate = TRUE, but is the output exponenitated? 
```{r sensory nb tidy table}
sensory_tidy_nb <- m1nb %>% 
  tidy(
    conf.int = TRUE,
    exponentiate = TRUE
    ) %>% 
  mutate(
    Variable =
  recode_factor(
    term,
    "patients_biological_sexFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
    )
  ) %>% 
  select( 
    Variable,
    Estimate = estimate,
    SE = std.error,
    z_value = statistic,
    p_value = p.value,
    CI_low = conf.low, 
    CI_high = conf.high
  )
    
kable(sensory_tidy_nb)
```

Check diagnostic plots 
```{r sensory glm diagnostic plots}
sensory.glm.diag <- glm.diag.plots(m1nb)
sensory.glm.diag
```


## lack of interest driver
###Linear regression

Run linear regression
However, due to the distribution of the outcome variable we will run and report negative binomial regressions
```{r lack of interest lm}
m2 <- regression_sex_arfid_dat %>% 
  lm(formula = pardi.lack_of_interest_numeric ~ 
       patients_biological_sex + 
       child.parent.pre.age_yrs)

summary(m2)
```

Format tidy table
```{r lack interest tidy output}
interest_table <- m2 %>% 
  tidy() %>%
  mutate(
    Variable =
  recode_factor(
    term,
    "patients_biological_sexFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
  )
  ) %>%
  select(
    Variable,
    Estimate = estimate,
    SE = std.error,
    t_value = statistic,
    p_value = p.value
  )

kable(interest_table)
```

Box plot of the relationship between lack of interest in eating and food and patient's sex
Format without legend (as going to format with multiple other plots)
```{r lack interest boxplot}
g2 <- regression_sex_arfid_dat %>%
  drop_na(patients_biological_sex) %>%
  drop_na(pardi.lack_of_interest_numeric) %>% 
  ggplot(
    aes(
      x = patients_biological_sex, 
      y = pardi.lack_of_interest_numeric, 
      fill = patients_biological_sex
      )  
    ) + 
  geom_boxplot(
    show.legend = FALSE
  ) + 
  xlab("Patient's sex") + 
  ylab("PARDI-AR-Q score") + 
  labs(fill = "Patient's sex") + 
  scale_fill_manual(values=c("#1920FA",
                             "#FACE19")) +
  theme_minimal()

g2
```

diagnostic plots to check assumptions
```{r lack interest diagnostic plots}
plot(m2)
autoplot(m2)
```

###Negative Binomial regression 

```{r lack interest negative binomial regression}
m2nb <- 
  MASS::glm.nb(pardi.lack_of_interest_numeric ~ 
                 patients_biological_sex + 
                 child.parent.pre.age_yrs, 
               data = regression_sex_arfid_dat
               )

summary(m2nb)
```

Exponentiate the coefficients
```{r lack interest exp}
m2nb$family$linkinv(coef(m2nb))
```

As a percentage
```{r lack interest NB percentage}
round((m2nb$family$linkinv(coef(m2nb))-1)*100)
```

Pseudo r-squared 
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r lack interest nagelkerke}
nagelkerke(m2nb)
```

Tidy table of outcome 
```{r lack interest nb tidy table}
interest_tidy_nb <- m2nb %>% 
   tidy(
    conf.int = TRUE,
    exponentiate = TRUE
    ) %>% 
  mutate(
    Variable =
  recode_factor(
    term,
    "patients_biological_sexFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
    )
  ) %>%  
  select( 
    Variable,
    Estimate = estimate,
    SE = std.error,
    z_value = statistic, 
    p_value = p.value,
    CI_low = conf.low, 
    CI_high = conf.high
  )
kable(interest_tidy_nb)
```

GLM diagnostic plots
```{r lack interest glm diagnostic plots}
interest.glm.diag <- glm.diag.plots(m2nb)
interest.glm.diag
```


## Fear of aversive consequences
###Linear Regression
However, due to the distribution of the outcome variable we will run zero-inflated negative bionomial regressions

```{r fear lm}
m3 <- regression_sex_arfid_dat %>% 
  lm(formula = pardi.fear_of_aversive_consequences_numeric ~ 
       patients_biological_sex + 
       child.parent.pre.age_yrs)

summary(m3)
```

Run a linear regression filtering out 0's to compare to zero-inflated binomial regression model
```{r fear lm filtered without 0}
m3_without_zeros <- regression_sex_arfid_dat %>% 
  filter(pardi.fear_of_aversive_consequences_numeric != 0) %>%
  lm(
    formula =
      pardi.fear_of_aversive_consequences_numeric 
    ~ patients_biological_sex
    + child.parent.pre.age_yrs
    )

summary(m3_without_zeros)
```

Tidy output
```{r fear tidy output}
fear_table <- m3 %>% 
  tidy() %>%
  mutate(
    Variable =
  recode_factor(
    term,
    "patients_biological_sexFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
  )
  ) %>%
  select(
    Variable,
    Estimate = estimate,
    SE = std.error,
    t_value = statistic,
    p_value = p.value
  )

kable(fear_table)
```


Boxplot of relationship between fear of aversive consequences of eating and patient's sex
Format without legend (as going to format with multiple other plots)
```{r fear boxplot}
g3 <- regression_sex_arfid_dat %>%
  drop_na(patients_biological_sex) %>%
  drop_na(pardi.fear_of_aversive_consequences_numeric) %>%
  
  ggplot(aes(x = patients_biological_sex,
             y = pardi.fear_of_aversive_consequences_numeric, 
             fill = patients_biological_sex)) +
  geom_boxplot(
    show.legend = FALSE
  ) + 
  xlab("Patient's sex") + 
  ylab("PARDI-AR-Q score") + 
  labs(fill = "Patient's Sex") + 
  scale_fill_manual(values=c("#1920FA",
                             "#FACE19")) +
  theme_minimal()

g3 
```

diagnostic plots
```{r fear diagnostic plots}
plot(m3)
autoplot(m3)
```


###Zero-inflated negative binomial regression 

```{r fear zero infated negative binomial regr}
m3_zinb <- zeroinfl(pardi.fear_of_aversive_consequences_numeric ~ 
                      patients_biological_sex + 
                      child.parent.pre.age_yrs, 
                    data = regression_sex_arfid_dat,
                    dist = "negbin",
                    #  zero.dist = "binomial",
                    link = "logit")

summary(m3_zinb)
```

Error: No tidy method for objects of class zeroinfl
```{r fear zinb tidy}
#fear_tidy_zinb <- tidy(m3_zinb, 
#                     conf.int = TRUE)
#kable(fear_tidy_zinb)
```

Exponentiate zero inflated coefficients
```{r fear exp}
exp(coef((m3_zinb)))
```

Percentage
```{r fear ZINB as percentage}
round((exp(coef(m3_zinb))-1)*100)
```

Pseudo r-squared 
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r fear nagelkerke}
nagelkerke(m3_zinb)
```


Confidence Intervals
```{r fear confidence intervals}
confint(m3_zinb)
```

+++RW: How to exponentiate coefficients in this table and add confidence intervals? 
How to add the zero inflated part of the model? 
```{r create fear zinb table}
fear_of_aversive_consequences_zinb.coefs = as.data.frame(
  summary(m3_zinb)$coefficients$count[,1:4])

names(fear_of_aversive_consequences_zinb.coefs)[2] = "SE" 

names(fear_of_aversive_consequences_zinb.coefs)[3] = "z_score" 

names(fear_of_aversive_consequences_zinb.coefs)[4] = "p_value" 


setattr(
  fear_of_aversive_consequences_zinb.coefs, "row.names", c("(Intercept)", 
                                                            "Female", 
                                                            "Age [years]", 
                                                            "Log(theta)"))

fear_of_aversive_consequences_zinb.coefs
```



#Presentation of regression output

How to present the output of negative binomial regression and zero-inflated negative binomial regression
One table which includes the three regression models 
Use tab_model: 

https://cran.r-project.org/web/packages/sjPlot/vignettes/tab_model_estimates.html

Rename labels of explanatory variables for table
```{r rename labels of explanatory variables}
explanatory_labs <- c(
  `(Intercept)` = "Intercept",
  `patients_biological_sexFemale` = "Female",
  `child.parent.pre.age_yrs` = "Age (years)", 
  `count_(Intercept)` = "Intercept", 
  `count_patients_biological_sexFemale` = "Female",
  `count_child.parent.pre.age_yrs` = "Age (years)",
  `zero_(Intercept)` = "Intercept", 
  `zero_patients_biological_sexFemale`	 = "Female",
  `zero_child.parent.pre.age_yrs` = "Age (years)"
)
```

Format the table including two negative binomial regression and one zero-inflated negative binomial regression output
```{r format regression output table}
regression_output <- 
  tab_model(
  m1nb, 
  m2nb,
  m3_zinb,
  pred.labels = explanatory_labs,
  dv.labels = c("Sensory sensitivities",
                "Lack of interest in food", 
                "Fear of aversive consequences of eating"),
  string.pred = "Explanatory variable",
  string.ci = "CI (95%)",
  string.p = "p-value", 
  p.style = "numeric",
  digits.p = 4,
  string.est = "Exponentiated coefficient",
  emph.p = FALSE
  )
  
regression_output
```


```{r print regression table}
knit_print(regression_output)
```


All p-values of intercept are: 
0.000000000000002
Would I show these as: 
1. scientific notation: 2e-16 
2. round to 4 dec points: 0.0000
Manually edit these. 

Doesn't recognise that zero-inflated and negative binomial models are the same. Manually edit the table to remove white space in the fear of averive consequences regression columns. 


#Format plots
Format three histograms and three boxplots into one plot to include in dissertation write up. 

Using patchwork 
First combine each driver plots with subheadings
```{r patchwork sensory plots}
Sensory_plots <- 
  h1 + g1


Sensory_plots[[2]] = Sensory_plots[[2]] + 
  theme(axis.title.x = element_blank())

Sensory_plots <- Sensory_plots + 
  plot_layout(guides = "collect") + 
   plot_annotation(title = c("ARFID driver: sensory sensitivities"), 
                   tag_levels = 'A')

Sensory_plots
```

```{r sensory ggsave likert plot}
ggsave(
  filename = paste0("Sensory_plots", date, ".pdf"), 
  path = "../plots/",
  plot = Sensory_plots,
  device = "pdf",
  scale = 1,
  width = 10,
  height = 4.5,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```

```{r patchwork interest plots}
Interest_plots <- 
  h2 + g2


Interest_plots[[2]] = Interest_plots[[2]] + 
  theme(axis.title.x = element_blank())

Interest_plots <- Interest_plots + 
  plot_layout(guides = "collect") + 
   plot_annotation(title = c("ARFID driver: lack of interest in eating"))

Interest_plots
```

```{r interest ggsave likert plot}
ggsave(
  filename = paste0("Interest_plots", date, ".pdf"), 
  path = "../plots/",
  plot = Interest_plots,
  device = "pdf",
  scale = 1,
  width = 10,
  height = 4.5,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```

```{r patchwork fear plots}
Fear_plots <- 
  h3 + g3

Fear_plots[[2]] = Fear_plots[[2]] + 
  theme(axis.title.x = element_blank())

Fear_plots <- Fear_plots + 
  plot_layout(guides = "collect") + 
   plot_annotation(title = c("ARFID driver: fear of aversive consequences of eating"))

Fear_plots
```

```{r fear ggsave likert plot}
ggsave(
  filename = paste0("Fear_plots", date, ".pdf"), 
  path = "../plots/",
  plot = Fear_plots,
  device = "pdf",
  scale = 1,
  width = 10,
  height = 4.5,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```


```{r combine plots with patchwork}
ARFID_driver_plots <- 
  Sensory_plots / 
  Interest_plots /
  Fear_plots

ARFID_driver_plots + 
  plot_layout(guides = "collect")
```



#format boxplots for poster presentation
```{r}
pardi_sex_boxplots <- 
  cowplot::plot_grid(g1, g2, g3,
                     labels = c("Sensory sensitivities", 
                                "Lack of interest", 
                                "Fear of aversive consequences"), 
                     label_size = 12, 
                     nrow = 1)
```

```{r}
ggsave(
  filename = paste0("pardi_sex_boxplots_poster", date, ".pdf"), 
  path = "../plots/",
  plot = pardi_sex_boxplots,
  device = "pdf",
  scale = 1,
  width = 13,
  height = 5,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```



## PARDI profile descriptive table by Sex

```{r select descriptive variables}
arfid_profile_dat <- arfid_dat %>% 
  select(child.parent.pre.biological_sex_of_your_child_at_birth_binary, 
         pardi.sensory_sensitivities_numeric, 
         pardi.lack_of_interest_numeric, 
         pardi.fear_of_aversive_consequences_numeric, 
         child.parent.pre.age_yrs) 
```

```{r Prepare table}
arfid_profile_table <- arfid_profile_dat %>% 
  tbl_summary(by = child.parent.pre.biological_sex_of_your_child_at_birth_binary, 
              label = list(pardi.sensory_sensitivities_numeric ~ 
                             "Avoidance of food based on sensory sensitivities", 
                           pardi.lack_of_interest_numeric ~
                             "Lack of interest in eating and food", 
                           pardi.fear_of_aversive_consequences_numeric ~
                             "Fear of aversive consequences of eating", 
                           child.parent.pre.age_yrs ~ 
                             "Patient's age in years"),
                
              type = list(pardi.sensory_sensitivities_numeric ~ 
                "continuous2",
              pardi.lack_of_interest_numeric ~
                "continuous2",
              pardi.fear_of_aversive_consequences_numeric ~
                "continuous2", 
              child.parent.pre.age_yrs ~ 
                "continuous2"),

              statistic = all_continuous2() ~ c(
                "{mean} ({SD})",
                "{median} ({p25}, {p75})"), 
              
              missing = "ifany")
```

```{r format and run table}
arfid_profile_table %>% 
  bold_labels() %>% 
  modify_header(label ~ "**ARFID profile**") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Patient's sex**")
```


