---
title: "ARFID and ASD"
author: "Rosie Watts"
date: "12/07/2021"
output:
  word_document: default
  html_document: default
---

#Set up R Markdown


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width='100%', out.height='100%')
```

Clear Global Environment 
```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Set current date 
```{r current date}
date <- Sys.Date()
```

Install necessary packages
```{r install packages}
#install.packages("knitr")
#install.packages("summarytools")
#install.packages("skimr")
#install.packages("psych")
#install.packages("gt")
#install.packages("sjPlot")
#install.packages("sjmisc")
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("gtsummary")
#install.packages("rcompanion")
#install.packages("patchwork")
#install.packages("car")
#install.packages("ggfortify")
#install.packages("broom")
#install.packages("MASS")
#install.packages("pscl")
#install.packaes("tidyverse")
```


Load necessary packages 
```{r load packages}
library(knitr)
library(skimr)
library(summarytools)
library(psych)
library(sjPlot)
library(ggplot2)
library(likert)
library(gtsummary)
library(rcompanion)
library(patchwork)
library(car)
library(ggfortify)
library(data.table)
library(broom) 
library(boot)
library(pscl)
library(tidyverse)
```



Read in data
```{r read in raw_data}
arfid_dat <- readRDS(file = "../data/arfid_data_clean2021-08-18.rds")
```

#Inspect the dataset

```{r skim}
arfid_dat %>% 
  skim()
```

ASD diagnoses are known to be more common in males, with females often being diagnosed at a later age. 

Check sex distribution in the various ASD categories
15 male and 15 female patients with ASD
```{r sex dist in ASD dx}
arfid_dat %>% 
  filter(ASD_diagnosis == "ASD diagnosis") %>% 
  freq(child.parent.pre.biological_sex_of_your_child_at_birth_binary)
```

13 males and 11 females with suspected ASD
```{r sex dist in suspected ASD}
arfid_dat %>% 
  filter(ASD_diagnosis == "Suspected ASD") %>% 
  freq(child.parent.pre.biological_sex_of_your_child_at_birth_binary)
```

31 males and 37 females with no comorbid ASD.
```{r sex dist in No ASD dx}
arfid_dat %>% 
  filter(ASD_diagnosis == "No ASD diagnosis") %>% 
  freq(child.parent.pre.biological_sex_of_your_child_at_birth_binary)
```

There is an even distribution of males and females in each ASD diagnosis category

+++CH: This could have been a crosstable

```{r}
arfid_dat %>%
  count(
    ASD_diagnosis,
    child.parent.pre.biological_sex_of_your_child_at_birth_binary
    )
```



#Check the distribution of the outcome variable
Check the distribution of each outcome variable for the regressions, plotted by ASD diagnosis

Sensory sensitivities
```{r sensory distribution histogram}
h1.asd <- arfid_dat %>% 
  drop_na(ASD_diagnosis) %>% 
  ggplot(aes(x = pardi.sensory_sensitivities_numeric, 
             fill = ASD_diagnosis)) +
  geom_histogram(position = position_dodge(preserve = "single")) + 
  labs(x = "PARDI-AR-Q score", 
       y = "Count", 
       fill = "ASD diagnosis") +
  theme_minimal()

h1.asd
```
The sensory sensitivities driver outcome variable has a negatively skewed distribution


Lack of interest
```{r interest distribution histogram}
h2.asd <- arfid_dat %>% 
  drop_na(ASD_diagnosis) %>% 
  ggplot(aes(x = pardi.lack_of_interest_numeric, 
             fill = ASD_diagnosis)) +
  geom_histogram(position = position_dodge(preserve = "single")) + 
  labs(x = "PARDI-AR-Q score", 
       y = "Count", 
       fill = "ASD diagnosis") +
  theme_minimal()

h2.asd
```
The lack of interest driver outcome variable has a negatively skewed distribution


Fear of aversive consequences
```{r fear distribution histogram}
h3.asd <- arfid_dat %>% 
  drop_na(ASD_diagnosis) %>% 
  ggplot(aes(x = pardi.fear_of_aversive_consequences_numeric, 
             fill = ASD_diagnosis)) +
  geom_histogram(position = position_dodge(preserve = "single")) + 
  labs(x = "PARDI-AR-Q score", 
       y = "Count", 
       fill = "ASD diagnosis") +
  #scale_fill_manual(values=c("#66c2a5", 
  #                           "#fc8d62", 
  #                           "#8da0cb")
  #                  ) +
  theme_minimal()

h3.asd
```
The fear of aversive consequences driver outcome score has a zero-inflated distribution. 


The sensory sensitivity and lack of interest variables are negatively distributed. 
The fear of aversive consequences variable has a zero-inflated distribution. 


#Likert plot for endorsement of PARDI items (ASD)
Grouped by comorbid ASD diagnosis (no = 0, suspected ASD= 1, ASD = 2)

##ASD
Filter patients who have an autism diagnosis and select variables to plot
```{r filter by ASD dx and select variables}
arfid_dat_likert_ASD <- arfid_dat %>% 
  
  filter(ASD_diagnosis ==
           "ASD diagnosis") %>%
  
  select(
    pardi.parent.pre.interactions_people_eating_difficulties,
    pardi.parent.pre.difficult_social_situations_social,
    pardi.parent.pre.taste_variation_sensitive_past,
    pardi.parent.pre.consistency_sensitive_past_month,
    pardi.parent.pre.appearance_sensitive_past_month,
    pardi.parent.pre.child_forgotten_forgotten_make,
    pardi.parent.pre.child_appeared_lack_enjoyment,
    pardi.parent.pre.stopped_eating_early_finished,
    pardi.parent.pre.affected_choking_pain_type,
    pardi.parent.pre.child_avoided_eating_situations,
    pardi.parent.pre.child_expressed_panic_physical) %>% 
  
    rename(
    "Difficulties: interactions with others" =
    pardi.parent.pre.interactions_people_eating_difficulties,
    "Difficulty: social situations" =
    pardi.parent.pre.difficult_social_situations_social,
    "Sensory sensitivity: taste" =
    pardi.parent.pre.taste_variation_sensitive_past,
    "Sensory sensitivity: texture" =
    pardi.parent.pre.consistency_sensitive_past_month,
    "Sensory sensitivity: appearance" =
    pardi.parent.pre.appearance_sensitive_past_month,
    "Forgotten to eat" = 
    pardi.parent.pre.child_forgotten_forgotten_make,
    "Lacked enjoyment in food" = 
    pardi.parent.pre.child_appeared_lack_enjoyment,
    "Stopped eating early" = 
    pardi.parent.pre.stopped_eating_early_finished,
    "Afraid something bad might happen" = 
    pardi.parent.pre.affected_choking_pain_type,
    "Avoided eating due to such worries" = 
    pardi.parent.pre.child_avoided_eating_situations,
    "Physical feelings of panic and anxiety" = 
    pardi.parent.pre.child_expressed_panic_physical)
  

arfid_dat_likert_ASD
```

Format Likert data
```{r format ASD likert data}
ASD_likert_data <- likert(arfid_dat_likert_ASD)
```

Plot with Likert plot using likert.bar.plot from the Likert package
```{r ASD likert plot }
ASD.likert.plot <- 
  likert.bar.plot(ASD_likert_data,
                  colors = 
                  c("#fef0d9", 
                    "#fdd49e", 
                    "#fdbb84",
                    "#fc8d59",
                    "#ef6548",
                    "#d7301f",
                    "#990000"),
                  plot.percent.neutral = FALSE,
                  text.color = "black",
                  text.size = 3,
                  ordered = FALSE, 
                  group.order = c(
                    "Difficulties: interactions with others", 
                    "Difficulty: social situations",
                    "Sensory sensitivity: taste",
                    "Sensory sensitivity: texture", 
                    "Sensory sensitivity: appearance", 
                    "Forgotten to eat", 
                    "Lacked enjoyment in food", 
                    "Stopped eating early", 
                    "Afraid something bad might happen", 
                    "Avoided eating due to such worries", 
                    "Physical feelings of panic and anxiety")
                  ) + 
  labs(y = "Endorsement (%)", 
       x = "PARDI-AR-Q item", 
       title = "Comorbid ASD diagnosis", 
       subtitle = "n = 28") +
  theme_minimal() 

ASD.likert.plot$layers[[1]]$geom_params$width = 0.7
ASD.likert.plot$layers[[2]]$geom_params$width = 0.7
ASD.likert.plot$layers[[3]]$geom_params$width = 0.7
ASD.likert.plot$layers[[4]]$geom_params$width = 0.7
ASD.likert.plot$layers[[5]]$geom_params$width = 0.7

ASD.likert.plot
```

Check frequencies against the likert plots to ensure this worked! 
```{r check frequencies}
arfid_dat_likert_ASD %>% 
  freq()
```
It worked - dropped category 3 from percentage report 
Level 0, 1, 2 - % reported to the left, 
Level 3 - percent dropped, 
Level 4, 4, 6 - % reported to the right. 


##No ASD diagnosis
Filter patients who do not have an ASD diagnosis and select variables to plot
```{r filter by no ASD dx and select variables}
arfid_dat_likert_noASD <- arfid_dat %>% 
  
  filter(ASD_diagnosis ==
           "No ASD diagnosis") %>%
  
  select(
    pardi.parent.pre.interactions_people_eating_difficulties,
    pardi.parent.pre.difficult_social_situations_social,
    pardi.parent.pre.taste_variation_sensitive_past,
    pardi.parent.pre.consistency_sensitive_past_month,
    pardi.parent.pre.appearance_sensitive_past_month,
    pardi.parent.pre.child_forgotten_forgotten_make,
    pardi.parent.pre.child_appeared_lack_enjoyment,
    pardi.parent.pre.stopped_eating_early_finished,
    pardi.parent.pre.affected_choking_pain_type,
    pardi.parent.pre.child_avoided_eating_situations,
    pardi.parent.pre.child_expressed_panic_physical) %>% 
  
    rename(
    "Difficulties: interactions with others" =
    pardi.parent.pre.interactions_people_eating_difficulties,
    "Difficulty: social situations" =
    pardi.parent.pre.difficult_social_situations_social,
    "Sensory sensitivity: taste" =
    pardi.parent.pre.taste_variation_sensitive_past,
    "Sensory sensitivity: texture" =
    pardi.parent.pre.consistency_sensitive_past_month,
    "Sensory sensitivity: appearance" =
    pardi.parent.pre.appearance_sensitive_past_month,
    "Forgotten to eat" = 
    pardi.parent.pre.child_forgotten_forgotten_make,
    "Lacked enjoyment in food" = 
    pardi.parent.pre.child_appeared_lack_enjoyment,
    "Stopped eating early" = 
    pardi.parent.pre.stopped_eating_early_finished,
    "Afraid something bad might happen" = 
    pardi.parent.pre.affected_choking_pain_type,
    "Avoided eating due to such worries" = 
    pardi.parent.pre.child_avoided_eating_situations,
    "Physical feelings of panic and anxiety" = 
    pardi.parent.pre.child_expressed_panic_physical)
  

arfid_dat_likert_noASD
```

Format Likert data
```{r format noASD likert data}
noASD_likert_data <- likert(arfid_dat_likert_noASD)
noASD_likert_data
```

Likert plot
```{r noASD likert plot}
noASD.likert.plot <- 
  likert.bar.plot(noASD_likert_data, 
                  colors = 
                  c("#fef0d9", 
                    "#fdd49e", 
                    "#fdbb84",
                    "#fc8d59",
                    "#ef6548",
                    "#d7301f",
                    "#990000"),
                  plot.percent.neutral = FALSE,
                  text.color = "black",
                  text.size = 3,
                  ordered = FALSE, 
                  group.order = c(
                    "Difficulties: interactions with others", 
                    "Difficulty: social situations",
                    "Sensory sensitivity: taste",
                    "Sensory sensitivity: texture", 
                    "Sensory sensitivity: appearance", 
                    "Forgotten to eat", 
                    "Lacked enjoyment in food", 
                    "Stopped eating early", 
                    "Afraid something bad might happen", 
                    "Avoided eating due to such worries", 
                    "Physical feelings of panic and anxiety")
                  ) + 
  labs(y = "Endorsement (%)", 
       x = "PARDI-AR-Q item", 
       title = "No comorbid diagnosis of ASD", 
       subtitle = "n = 49") +
  theme_minimal() 

#Format width of barchart 
noASD.likert.plot$layers[[1]]$geom_params$width = 0.7
noASD.likert.plot$layers[[2]]$geom_params$width = 0.7
noASD.likert.plot$layers[[3]]$geom_params$width = 0.7
noASD.likert.plot$layers[[4]]$geom_params$width = 0.7
noASD.likert.plot$layers[[5]]$geom_params$width = 0.7


noASD.likert.plot
```


##Suspected ASD
Filter patients who have suspected ASD and select variables to plot
```{r filter suspected ASD}
arfid_dat_likert_sxASD <- arfid_dat %>% 
  
  filter(ASD_diagnosis ==
           "Suspected ASD") %>%
  
  select(
    pardi.parent.pre.interactions_people_eating_difficulties,
    pardi.parent.pre.difficult_social_situations_social,
    pardi.parent.pre.taste_variation_sensitive_past,
    pardi.parent.pre.consistency_sensitive_past_month,
    pardi.parent.pre.appearance_sensitive_past_month,
    pardi.parent.pre.child_forgotten_forgotten_make,
    pardi.parent.pre.child_appeared_lack_enjoyment,
    pardi.parent.pre.stopped_eating_early_finished,
    pardi.parent.pre.affected_choking_pain_type,
    pardi.parent.pre.child_avoided_eating_situations,
    pardi.parent.pre.child_expressed_panic_physical) %>% 
  
    rename(
    "Difficulties: interactions with others" =
    pardi.parent.pre.interactions_people_eating_difficulties,
    "Difficulty: social situations" =
    pardi.parent.pre.difficult_social_situations_social,
    "Sensory sensitivity: taste" =
    pardi.parent.pre.taste_variation_sensitive_past,
    "Sensory sensitivity: texture" =
    pardi.parent.pre.consistency_sensitive_past_month,
    "Sensory sensitivity: appearance" =
    pardi.parent.pre.appearance_sensitive_past_month,
    "Forgotten to eat" = 
    pardi.parent.pre.child_forgotten_forgotten_make,
    "Lacked enjoyment in food" = 
    pardi.parent.pre.child_appeared_lack_enjoyment,
    "Stopped eating early" = 
    pardi.parent.pre.stopped_eating_early_finished,
    "Afraid something bad might happen" = 
    pardi.parent.pre.affected_choking_pain_type,
    "Avoided eating due to such worries" = 
    pardi.parent.pre.child_avoided_eating_situations,
    "Physical feelings of panic and anxiety" = 
    pardi.parent.pre.child_expressed_panic_physical)
  

arfid_dat_likert_sxASD
```

Likert data
```{r format sxASD likert data}
sxASD_likert_data <- likert(arfid_dat_likert_sxASD)
sxASD_likert_data
```

Likert plot
```{r sxASD likert plot}
sxASD.likert.plot <- 
  likert.bar.plot(sxASD_likert_data, 
                  colors = 
                  c("#fef0d9", 
                    "#fdd49e", 
                    "#fdbb84",
                    "#fc8d59",
                    "#ef6548",
                    "#d7301f",
                    "#990000"),
                  plot.percent.neutral = FALSE,
                  text.color = "black",
                  text.size = 3,
                  ordered = FALSE, 
                  group.order = c(
                    "Difficulties: interactions with others", 
                    "Difficulty: social situations",
                    "Sensory sensitivity: taste",
                    "Sensory sensitivity: texture", 
                    "Sensory sensitivity: appearance", 
                    "Forgotten to eat", 
                    "Lacked enjoyment in food", 
                    "Stopped eating early", 
                    "Afraid something bad might happen", 
                    "Avoided eating due to such worries", 
                    "Physical feelings of panic and anxiety")
                  ) + 
  labs(y = "Endorsement (%)", 
       x = "PARDI-AR-Q item", 
       title = "Suspected ASD", 
       subtitle = "n = 21") +
  theme_minimal() 


sxASD.likert.plot$layers[[1]]$geom_params$width = 0.7
sxASD.likert.plot$layers[[2]]$geom_params$width = 0.7
sxASD.likert.plot$layers[[3]]$geom_params$width = 0.7
sxASD.likert.plot$layers[[4]]$geom_params$width = 0.7
sxASD.likert.plot$layers[[5]]$geom_params$width = 0.7


sxASD.likert.plot
```

Create a likert plot with legend at the bottom to use for dissertation
```{r}
legend <- 
  likert.bar.plot(sxASD_likert_data, 
                  colors = 
                  c("#fef0d9", 
                    "#fdd49e", 
                    "#fdbb84",
                    "#fc8d59",
                    "#ef6548",
                    "#d7301f",
                    "#990000"),
                  plot.percent.neutral = FALSE,
                  text.color = "black",
                  text.size = 3,
                  ordered = FALSE, 
                  legend.position = "bottom",
                  group.order = c(
                    "Difficulties: interactions with others", 
                    "Difficulty: social situations",
                    "Sensory sensitivity: taste",
                    "Sensory sensitivity: texture", 
                    "Sensory sensitivity: appearance", 
                    "Forgotten to eat", 
                    "Lacked enjoyment in food", 
                    "Stopped eating early", 
                    "Afraid something bad might happen", 
                    "Avoided eating due to such worries", 
                    "Physical feelings of panic and anxiety"
                    )) + 
  labs(y = "Endorsement (%)", 
       x = "PARDI-AR-Q item", 
       title = "Legend for cowplot"
  )
```


##ASD, sx ASD and non-ASD

Format with cowplot 
```{r cowplot likert}
legend <- cowplot::get_legend(legend)

ASD_likert_cowplot <- 
  cowplot::plot_grid(ASD.likert.plot + theme(legend.position="none"),
                     noASD.likert.plot + theme(legend.position="none"), 
                     sxASD.likert.plot + theme(legend.position="none"),
                     legend,
                     ncol = 1, 
                     align = "v")

ASD_likert_cowplot
```


Use ggplot to save likert plot formatted by cowplot:
```{r ggsave likert cowplot}
ggsave(
  filename = paste0("likert_plot_ASD_cowplot", date, ".pdf"),
  plot = ASD_likert_cowplot,
  path = "../plots/",
  device = "pdf",
  scale = 1,
  width = 7,
  height = 14,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```



#Regressions 
Three regressions will be computed to examine the effect of comorbid ASD on the PARDI profile scores, whilst controlling for the patient's age and sex 
1. Sensory sensitivity profile (0 - 18)
2. Lack of interest profile (0 - 18)
3. Fear of aversive consequences profile (0 - 18)


ASD binary = 
`0` = "No ASD diagnosis",
`1` = "Suspected ASD", 
`2` = "ASD diagnosis

```{r select variables}
regression_asd_arfid_dat <- arfid_dat %>% 
  select(pardi.sensory_sensitivities_numeric,
         pardi.lack_of_interest_numeric, 
         pardi.fear_of_aversive_consequences_numeric,
         ASD_diagnosis,
         child.parent.pre.biological_sex_of_your_child_at_birth_binary,
         child.parent.pre.age_yrs) 
```


##Sensory sensitivity
###Linear regression
Run linear regression 
However, due to the distribution of the outcome variable we will run and report negative bionomial regressions
```{r sensory lm}
m1 <- regression_asd_arfid_dat %>% 
  lm(formula = pardi.sensory_sensitivities_numeric ~ 
       ASD_diagnosis +
       child.parent.pre.biological_sex_of_your_child_at_birth_binary + 
       child.parent.pre.age_yrs)

summary(m1)
```

Tidy table
```{r sensory tidy table}
sensory_table_asd <- m1 %>%
  tidy() %>%
  mutate(
    Variable =
  recode_factor(
    term,
    "ASD_diagnosisSuspected ASD" = "Suspected ASD",
    "ASD_diagnosisASD diagnosis" = "Comorbid ASD diagnosis",
    "child.parent.pre.biological_sex_of_your_child_at_birth_binaryFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
  )
  ) %>%
  select(
    Variable,
    Estimate = estimate,
    SE = std.error,
    t_value = statistic,
    p_value = p.value
  )

kable(sensory_table_asd)
```

Box plot to visualise the relationship between sensory sensitivity and ASD diagnosis
drop legend for later formatting 
```{r sensory boxplot}
g1.asd <- regression_asd_arfid_dat %>%
  drop_na(ASD_diagnosis) %>%
  drop_na(pardi.sensory_sensitivities_numeric) %>%
  
  ggplot(aes(x = ASD_diagnosis,
             y = pardi.sensory_sensitivities_numeric, 
             fill = ASD_diagnosis)) +
  geom_boxplot(
    show.legend = FALSE
  ) + 
  xlab("Comorbid ASD diagnosis") + 
  ylab("PARDI-AR-Q score") + 
  labs(fill = "Comorbid ASD diagnosis") + 
  theme_minimal()

g1.asd
```

Check assumptions 
```{r multicollinearity}
vif(m1)
```

```{r sensory diagnostic plots}
plot(m1)
autoplot(m1)
```


###Negative Binomial Regressions
Due to the distribution of the outcome variable, negative binomial regressions will also be computed and the model compared with linear regression
```{r sensory negative binomial regression}
m1nb <- 
  MASS::glm.nb(pardi.sensory_sensitivities_numeric ~ 
           ASD_diagnosis +
           child.parent.pre.biological_sex_of_your_child_at_birth_binary + 
           child.parent.pre.age_yrs,
           data = regression_asd_arfid_dat
               )

summary(m1nb)
```

Exponentiated output
```{r sensory NB regression exponentiate output}
m1nb$family$linkinv(coef(m1nb))
```

Exponentiated coefficient as a percentage
```{r sensory percentage}
round((m1nb$family$linkinv(coef(m1nb))-1)*100)
```

Pseudo r-squared 
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r sensory r2 nagelkerke}
nagelkerke(m1nb)
```

Tidy table output
I don't use these tables in the end (instead I use tab_model - at the end of the script)
```{r sensory nb table}
sensory_asd_tidy_nb <- m1nb %>% 
  tidy(
    conf.int = TRUE, 
    expoentiate = TRUE
    ) %>%
  mutate(
    Variable =
  recode_factor(
    term,
    "ASD_diagnosisSuspected ASD" = "Suspected ASD",
    "ASD_diagnosisASD diagnosis" = "Comorbid ASD diagnosis",
    "child.parent.pre.biological_sex_of_your_child_at_birth_binaryFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
  )
  ) %>%
  select( 
    Variable,
    Estimate = estimate,
    SE = std.error,
    z_value = statistic,
    p_value = p.value,
    CI_low = conf.low, 
    CI_high = conf.high
  )
                             
kable(sensory_asd_tidy_nb)
```


```{r sensory glm diagnostic plots}
sensory.asd.glm.diag <- glm.diag.plots(m1nb)
sensory.asd.glm.diag
```


##Lack of interest 
###Linear regression

```{r lack of interest lm}
m2 <- regression_asd_arfid_dat %>% 
  lm(formula = pardi.lack_of_interest_numeric ~ 
       ASD_diagnosis +
       child.parent.pre.biological_sex_of_your_child_at_birth_binary + 
       child.parent.pre.age_yrs)

summary(m2)
```

tidy table
```{r lack interest tidy table}
interest_table_asd <- tidy(m2)
kable(interest_table_asd)
```

Box plot of relationship between lack of interest ARFID score and comorbid ASD diagnosis 
```{r lack interest boxplot}
g2.asd <- regression_asd_arfid_dat %>%
  drop_na(ASD_diagnosis) %>%
  drop_na(pardi.lack_of_interest_numeric) %>%
  
  ggplot(aes(x = ASD_diagnosis,
             y = pardi.lack_of_interest_numeric, 
             fill = ASD_diagnosis)) +
  geom_boxplot(
    show.legend = FALSE
  ) + 
  xlab("Comorbid ASD diagnosis") + 
  ylab("PARDI-AR-Q score") + 
  labs(fill = "Comorbid ASD diagnosis") + 
  theme_minimal()

g2.asd
```

diagnostic plots
```{r lack interest diagnostic plots}
plot(m2)
autoplot(m2)
```


###Negative binomial regression 
```{r lack interest negative binomial regression}
m2nb <-
  MASS::glm.nb(pardi.lack_of_interest_numeric ~ 
                 ASD_diagnosis +
                 child.parent.pre.biological_sex_of_your_child_at_birth_binary + 
                 child.parent.pre.age_yrs, 
               data = regression_asd_arfid_dat
               )

summary(m2nb)
```

Exponentiated output
```{r lack interest NB regression exponentiate output}
m2nb$family$linkinv(coef(m2nb))
```

As a percentage
```{r lack interest percentage}
round((m2nb$family$linkinv(coef(m2nb))-1)*100)
```

Pseudo r-squared 
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r lack interest r2 nagelkerke}
nagelkerke(m2nb)
```

Tidy table
```{r lack interest m2nb table}
interest_tidy_nb <- m2nb %>% 
  tidy(
    conf.int = TRUE, 
    exponentiate = TRUE
    ) %>%
  mutate(
    Variable =
  recode_factor(
    term,
    "ASD_diagnosisSuspected ASD" = "Suspected ASD",
    "ASD_diagnosisASD diagnosis" = "Comorbid ASD diagnosis",
    "child.parent.pre.biological_sex_of_your_child_at_birth_binaryFemale" = "Female",
    "child.parent.pre.age_yrs" = "Age [years]"
  )
  ) %>%
  select( 
    Variable,
    Estimate = estimate,
    SE = std.error,
    z_value = statistic,
    p_value = p.value,
    CI_low = conf.low, 
    CI_high = conf.high
  )
kable(interest_tidy_nb) 
```


```{r lack interest glm diagnostic plots}
interest.asd.glm.diag <- glm.diag.plots(m2nb)
interest.asd.glm.diag
```


##Fear of aversive consequences
### Linear regression

```{r fear consequences lm}
m3 <- regression_asd_arfid_dat %>% 
  lm(formula = pardi.fear_of_aversive_consequences_numeric ~ 
       ASD_diagnosis +
       child.parent.pre.biological_sex_of_your_child_at_birth_binary + 
       child.parent.pre.age_yrs)

summary(m3)
```

tidy table
```{r fear table}
fear_table_asd <- tidy(m3)
kable(fear_table_asd)
```

Box plot of relationship between fear of aversive consequences and comorbid ASD
```{r fear boxplot}
g3.asd <- regression_asd_arfid_dat %>%
  drop_na(ASD_diagnosis) %>%
  drop_na(pardi.fear_of_aversive_consequences_numeric) %>%
  
  ggplot(aes(x = ASD_diagnosis,
             y = pardi.fear_of_aversive_consequences_numeric, 
             fill = ASD_diagnosis)) +
  geom_boxplot(
    show.legend = FALSE
  ) + 
  xlab("Comorbid ASD diagnosis") + 
  ylab("PARDI-AR-Q score") + 
  labs(fill = "Comorbid ASD diagnosis") + 
  theme_minimal()

g3.asd
```

diagnostic plots
```{r fear diagnostic plots}
plot(m3)
autoplot(m3)
```

### Zero inflated negative binomial regression 
Fear of aversive consequences profile score has a zero-inflated model and therefore a zero-inflated negative binomial regression was also computed
```{r fear zero infated negative binomial regr}
m3_zinb <- zeroinfl(pardi.fear_of_aversive_consequences_numeric ~ 
                      ASD_diagnosis +
                      child.parent.pre.biological_sex_of_your_child_at_birth_binary + 
                      child.parent.pre.age_yrs, 
                    data = regression_asd_arfid_dat,
                    dist = "negbin",
                    #zero.dist = "binomial", # ? 
                    link = "logit")

summary(m3_zinb)
```

Table alternative for zero inflation models
Error: No tidy method for objects of class zeroinfl

```{r fear zinb tidy table}
#fear_zinb_tidy <- tidy(m3_zinb, 
#                       conf.int = TRUE) 
#kable(fear_zinb_tidy)
```

```{r fear ZINB regression exponentiated output}
exp(coef(m3_zinb))
```

As a percentage
```{r Fear percentage}
round((exp(coef(m3_zinb))-1)*100)
```

Pseudo r-squared 
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r fear nagelkerke}
nagelkerke(m3_zinb)
```


Create tidy table manually:

```{r Fear ZINB summary output}
fear_of_aversive_consequences_asd_zinb.coefs = as.data.frame(
  summary(m3_zinb)$coefficients$count[,1:4])

names(fear_of_aversive_consequences_asd_zinb.coefs)[2] = "SE" 

names(fear_of_aversive_consequences_asd_zinb.coefs)[3] = "z_score" 

names(fear_of_aversive_consequences_asd_zinb.coefs)[4] = "p_value" 


setattr(
  fear_of_aversive_consequences_asd_zinb.coefs, 
  "row.names", 
  c(
    "(Intercept)", 
    "Female", 
    "Age [years]", 
    "Log(theta)"
    )
  )

fear_of_aversive_consequences_asd_zinb.coefs
```


#Format regression outputs 

To present regression output summarise findings in one table with the three models
Two negative binomial regressions, one zero-inflated negative binomial regression
Use tab_model

Rename explanatory variables for the table 
```{r rename explanatory variables}
predictor_labs <- c(
  `(Intercept)` = "Intercept",
  `ASD_diagnosisSuspected ASD` = "Suspected ASD", 
  `ASD_diagnosisASD diagnosis` = "Comorbid ASD diagnosis",
  `child.parent.pre.biological_sex_of_your_child_at_birth_binaryFemale` = "Female",
  `child.parent.pre.age_yrs` = "Age (years)", 
  `count_(Intercept)` = "Intercept", 
  `count_ASD_diagnosisSuspected ASD` = "Suspected ASD", 
  `count_ASD_diagnosisASD diagnosis` = "Comorbid ASD diagnosis", 
  `count_child.parent.pre.biological_sex_of_your_child_at_birth_binaryFemale` = "Female", 
  `count_child.parent.pre.age_yrs` = "Age (years)", 
  `zero_(Intercept)` = "Intercept", 
  `zero_ASD_diagnosisSuspected ASD` = "Suspected ASD", 
  `zero_ASD_diagnosisASD diagnosis` = "Comorbid ASD diagnosis", 
  `zero_child.parent.pre.biological_sex_of_your_child_at_birth_binaryFemale` = "Female", 
  `zero_child.parent.pre.age_yrs` = "Age (years)"
  )
```

Format table
```{r format regression table using tab_model}
regression_output_asd <- 
  tab_model(
  m1nb, 
  m2nb,
  m3_zinb,
  pred.labels = predictor_labs,
  dv.labels = c("Sensory sensitivities",
                "Lack of interest in eating", 
                "Fear of aversive consequences of eating"),
  string.pred = "Explanatory variable",
  string.ci = "CI (95%)",
  string.p = "p-value", 
  p.style = "numeric",
  digits.p = 4,
  string.est = "Exponentiated coefficient",
  emph.p = FALSE
  )
  
  
regression_output_asd
```

```{r print table}
knit_print(regression_output_asd)
```


Need to manually format: 
a. p-values below 0.001
b. white space in the zero-inflated negaitve binomial model


#Format plots
Create one plot for the three histograms (outcome variable distributions) and the three box plots (ASD group for each of the outcome variables)

Using patchwork
Individually format sensory plots
```{r patchwork sensory plots}
Sensory_plots_asd <- 
  h1.asd + g1.asd

Sensory_plots_asd[[2]] = Sensory_plots_asd[[2]] + 
  theme(axis.title.x = element_blank())

Sensory_plots_asd <- Sensory_plots_asd + 
  plot_layout(guides = "collect") + 
   plot_annotation(title = c("ARFID driver: sensory sensitivities"))

Sensory_plots_asd
```

Save the sensory plots
```{r sensory ggsave likert plot}
ggsave(
  filename = paste0("Sensory_plots_asd", date, ".pdf"), 
  path = "../plots/",
  plot = Sensory_plots_asd,
  device = "pdf",
  scale = 1,
  width = 10,
  height = 4, #or 3.8?
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```

Individually format lack of interest plots
```{r patchwork interest plots}
Interest_plots_asd <- 
  h2.asd + g2.asd


Interest_plots_asd[[2]] = Interest_plots_asd[[2]] + 
  theme(axis.title.x = element_blank())

Interest_plots_asd <- Interest_plots_asd + 
  plot_layout(guides = "collect") + 
   plot_annotation(title = c("ARFID driver: lack of interest in eating"))

Interest_plots_asd
```

```{r Interest ggsave likert plot}
ggsave(
  filename = paste0("Interest_plots_asd", date, ".pdf"), 
  path = "../plots/",
  plot = Interest_plots_asd,
  device = "pdf",
  scale = 1,
  width = 10,
  height = 4, #or 3.8?
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```

Individually format fear of aversive consequences plots
```{r patchwork fear plots}
Fear_plots_asd <- 
  h3.asd + g3.asd


Fear_plots_asd[[2]] = Fear_plots_asd[[2]] + 
  theme(axis.title.x = element_blank())

Fear_plots_asd <- Fear_plots_asd + 
  plot_layout(guides = "collect") + 
   plot_annotation(title = c("ARFID driver: fear of aversive consequences"))

Fear_plots_asd
```

```{r fear ggsave likert plot}
ggsave(
  filename = paste0("Fear_plots_asd", date, ".pdf"), 
  path = "../plots/",
  plot = Fear_plots_asd,
  device = "pdf",
  scale = 1,
  width = 10,
  height = 4, #or 3.8?
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```


#format boxplots for poster presentation
```{r}
pardi_ASD_boxplots <- 
  cowplot::plot_grid(g1.asd, 
                     g2.asd, 
                     g3.asd,
                     labels = c("Sensory sensitivities", 
                                "Lack of interest", 
                                "Fear of aversive consequences"), 
                     label_size = 12, 
                     nrow = 1)
```

```{r}
ggsave(
  filename = paste0("pardi_ASD_boxplots_poster", date, ".pdf"), 
  path = "../plots/",
  plot = pardi_ASD_boxplots,
  device = "pdf",
  scale = 1,
  width = 13,
  height = 5,
  dpi = 300,
  limitsize = FALSE,
  bg = NULL
  )
```


#Comparative table

Summary statistics table to compare the ARFID drivers in patients with ASD, comorbid ASD and no-asd

```{r select ARFID profiles}
arfid_profile <- arfid_dat %>% 
  select(ASD_diagnosis,
         pardi.sensory_sensitivities_numeric, 
         pardi.lack_of_interest_numeric, 
         pardi.fear_of_aversive_consequences_numeric, 
         child.parent.pre.biological_sex_of_your_child_at_birth_binary, 
         child.parent.pre.age_yrs)
```


```{r Prepare table}
arfid_profile_table <- arfid_profile %>% 
  tbl_summary(by = ASD_diagnosis, 
              label = list(pardi.sensory_sensitivities_numeric ~ 
                             "Avoidance of food based on sensory sensitivities", 
                           pardi.lack_of_interest_numeric ~
                             "Lack of interest in eating and food", 
                           pardi.fear_of_aversive_consequences_numeric ~
                             "Fear of aversive consequences of eating", 
                           child.parent.pre.biological_sex_of_your_child_at_birth_binary ~ 
                             "Patient's biological sex",
                           child.parent.pre.age_yrs ~ 
                             "Patient's age in years"),
                
              type = list(pardi.sensory_sensitivities_numeric ~ 
                "continuous2",
              pardi.lack_of_interest_numeric ~
                "continuous2",
              pardi.fear_of_aversive_consequences_numeric ~
                "continuous2", 
              child.parent.pre.biological_sex_of_your_child_at_birth_binary ~ 
                "categorical",
              child.parent.pre.age_yrs ~ 
                "continuous2"),

              statistic = all_continuous2() ~ c(
                "{mean} ({SD})",
                "{median} ({p25}, {p75})"), 
              
              missing = "always")
```


```{r format and run table}
arfid_profile_table %>% 
  bold_labels() %>%  
  modify_header(label ~ "**ARFID Profile**") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "Comorbid ASD Diagnosis")
```


